### 2016-05-20 Paper.tex
add tex

% This is "sig-alternate.tex" V2.1 April 2013
% This file should be compiled with V2.5 of "sig-alternate.cls" May 2012
%
% This example file demonstrates the use of the 'sig-alternate.cls'
% V2.5 LaTeX2e document class file. It is for those submitting
% articles to ACM Conference Proceedings WHO DO NOT WISH TO
% STRICTLY ADHERE TO THE SIGS (PUBS-BOARD-ENDORSED) STYLE.
% The 'sig-alternate.cls' file will produce a similar-looking,
% albeit, 'tighter' paper resulting in, invariably, fewer pages.
%
% ----------------------------------------------------------------------------------------------------------------
% This .tex file (and associated .cls V2.5) produces:
%       1) The Permission STATEment
%       2) The Conference (location) Info information
%       3) The Copyright Line with ACM data
%       4) NO page numbers
%
% as against the acm_proc_article-sp.cls file which
% DOES NOT produce 1) thru' 3) above.
%
% Using 'sig-alternate.cls' you have control, however, from within
% the source .tex file, over both the CopyrightYear
% (defaulted to 200X) and the ACM Copyright Data
% (defaulted to X-XXXXX-XX-X/XX/XX).
% e.g.
% \CopyrightYear{2007} will cause 2007 to appear in the copyright line.
% \crdata{0-12345-67-8/90/12} will cause 0-12345-67-8/90/12 to appear in the copyright line.
%
% ---------------------------------------------------------------------------------------------------------------
% This .tex source is an example which *does* use
% the .bib file (from which the .bbl file % is produced).
% REMEMBER HOWEVER: After having produced the .bbl file,
% and prior to final submission, you *NEED* to 'insert'
% your .bbl file into your source .tex file so as to provide
% ONE 'self-contained' source file.
%
% ================= IF YOU HAVE QUESTIONS =======================
% Questions regarding the SIGS styles, SIGS policies and
% procedures, Conferences etc. should be sent to
% Adrienne Griscti (griscti@acm.org)
%
% Technical questions _only_ to
% Gerald Murray (murray@hq.acm.org)
% ===============================================================
%
% For tracking purposes - this is V2.0 - May 2012

\documentclass{sig-alternate-05-2015}

\usepackage{enumitem}
\usepackage{algorithm}
\usepackage{algorithmic}
\usepackage{amsmath}
\DeclareMathOperator*{\argmax}{arg\,max}
\newcommand{\tabincell}[2]{\begin{tabular}{@{}#1@{}}#2\end{tabular}}
\renewcommand{\algorithmicrequire}{\textbf{Input:}} 
\renewcommand{\algorithmicensure}{\textbf{Output:}}
\begin{document}

% Copyright
\setcopyright{acmcopyright}
%\setcopyright{acmlicensed}
%\setcopyright{rightsretained}
%\setcopyright{usgov}
%\setcopyright{usgovmixed}
%\setcopyright{cagov}
%\setcopyright{cagovmixed}

% DOI
\doi{10.475/123_4}

% ISBN
\isbn{123-4567-24-567/08/06}

%Conference
\conferenceinfo{PLDI '13}{June 16--19, 2013, Seattle, WA, USA}

\acmPrice{\$15.00}

%
% --- Author Metadata here ---
\conferenceinfo{WOODSTOCK}{'97 El Paso, Texas USA}
%\CopyrightYear{2007} % Allows default copyright year (20XX) to be over-ridden - IF NEED BE.
%\crdata{0-12345-67-8/90/01}  % Allows default copyright data (0-89791-88-6/97/05) to be over-ridden - IF NEED BE.
% --- End of Author Metadata ---

\title{A Context-Aware Method for User Prediction in Shared Accounts for Recommendation}

%
% You need the command \numberofauthors to handle the 'placement
% and alignment' of the authors beneath the title.
%
% For aesthetic reasons, we recommend 'three authors at a time'
% i.e. three 'name/affiliation blocks' be placed beneath the title.
%
% NOTE: You are NOT restricted in how many 'rows' of
% "name/affiliations" may appear. We just ask that you restrict
% the number of 'columns' to three.
%
% Because of the available 'opening page real-eSTATE'
% we ask you to refrain from putting more than six authors
% (two rows with three columns) beneath the article title.
% More than six makes the first-page appear very cluttered indeed.
%
% Use the \alignauthor commands to handle the names
% and affiliations for an 'aesthetic maximum' of six authors.
% Add names, affiliations, addresses for
% the seventh etc. author(s) as the argument for the
% \additionalauthors command.
% These 'additional authors' will be output/set for you
% without further effort on your part as the last section in
% the body of your article BEFORE References or any Appendices.

\numberofauthors{3} %  in this sample file, there are a *total*
% of EIGHT authors. SIX appear on the 'first-page' (for formatting
% reasons) and the remaining two appear in the \additionalauthors section.
%
\author{
% You can go ahead and credit any number of authors here,
% e.g. one 'row of three' or two rows (consisting of one row of three
% and a second row of one, two or three).
%
% The command \alignauthor (no curly braces needed) should
% precede each author name, affiliation/snail-mail address and
% e-mail address. Additionally, tag each line of
% affiliation/address with \affaddr, and tag the
% e-mail address with \email.
%
% 1st. author
\alignauthor
XXX\\
       \affaddr{XXX}\\
       \affaddr{XX}\\
       \email{XXX}
% 2nd. author
\alignauthor
XXX\\
       \affaddr{XXX}\\
       \affaddr{XX}\\
       \email{XXX}
% 3rd. author
\alignauthor
XXX\\
       \affaddr{XXX}\\
       \affaddr{XX}\\
       \email{XXX}
}
% There's nothing stopping you putting the seventh, eighth, etc.
% author on the opening page (as the 'third row') but we ask,
% for aesthetic reasons that you place these 'additional authors'
% in the \additional authors block, viz.
% Just remember to make sure that the TOTAL number of authors
% is the number that will appear on the first page PLUS the
% number that will appear in the \additionalauthors section.

\maketitle
\begin{abstract}
Traditional recommender systems including collaborative filter and content-based method usually assume every account as a single user. However, under many circumstances, multiple users share a common account. Such as an online shopping account for family members and an online ticket booking account for family or companions. For the former case, service provider can't access user's personal information precisely. For the latter case, user's personal information can be acquired only after the user has submitted the order or checked in. If we can predict current user before he making a choice, then we may provide a more pertinent recommendation. For scenarios where user's within an account can't be identified precisely, there are some methods such as context aware methods and clustering. In this paper, we deal with the situation that user's personal information can be acquired. we propose a probabilistic method for user identification in a shared account with history behaviors and contextual knowledge. We then experimentally demonstrate its effectiveness on a dataset of Ctrip.com. The result show that our method outperforms conventional methods.
\end{abstract}

\keywords{recommender system, probabilistic topic model, shared account}

\section{Introduction}
Recent years, with the repaid development of online travel agency, there are more and more passengers booking tickets or hotels through online service provider. It is quite common that a user books tickets for the whole family or companions. Typically, an user may input his location, destination and departure time, then he will get a list of candidate items. In general, there are dozens of items within a list , all of them are isomorphic. Thus, it takes quite long time for an user to compare and choose the most approximate one. Therefore, a recommender system is quite necessary to be applied for better user experience. Figure 1 shows a list for all candidate flights departure from Beijing to Hong Kong. There are total 156 matching flights in result. The website only provides simple sorting strategies such as departure time, arrival time, price. Thus, it may take quite long time for users to find the appropriate one.\par
\begin{figure}[!hbt]
\centering
\includegraphics[scale=.48]{flight_tickets.eps}
\caption{Search result for flight tickets}
\label{fig:Prob}
\end{figure}\par
Essentially, an item recommender system is used for generating a personalized ranking on a set of items\cite{lv:rec}. Typical recommender systems assume that every account represents a single preference model. However, in many cases, multiple users will share one account. Depending on the service, some service providers can acquire user's personal information within an account precisely while others can't. For most online travel service providers, user's personal information can be acquired, for example, online airline ticket providers require users going aboard to fill in their personal information, and online hotel booking service providers can acquire users' personal information when they check in. It is likely that each user has different preference from each other. If we can identify users within a single account for current contextual environment, we may get the chance to improve accuracy of recommendation.\par
To the best of our knowledge, all existing methods focus on extracting implicit users within an account. Some researches\cite{kabbur:nlmf}\cite{jason:embedding} extract users applying nonlinear latent factorization. Some researches\cite{koen:top-n}\cite{yutaka:modeling} focus on user extraction with no context information. These methods always treat an account as a fixed count of implicit users, and the experiment result can be only evaluated on artificial composite datasets. In this article, we deal with the challenge that service providers can acquire a user's personal information only after he has submitted the order. Our goal is to predict distribution of users in current session based on history behavior and contextual knowledge, thus we can make more pertinent recommendation. To achieve this target, we propose a probabilistic author topic model to analyze users' behavior. We regard all orders in an account as corpus, all users in account as authors, orders as documents, content attributes of the items and contextual knowledge as item list. Author is a multinomial distribution over topics and topic is a multinomial distribution over items. Note that if an order has more than one user, these users are co-authors of this document.\par
In experiment section, we apply our method in a flight ticket order dataset of Ctrip, largest OTA service provider in China. In this dataset, we have submitted order as well as trace log in that session. And the result shows that our method has higher individual identification accuracy and a better recommendation accuracy.\par
This article provides following contributions:\\
\begin{enumerate}
\item We provide a probabilistic user identification method for the situation, where personal information within an account can be acquired.
\item We evaluate the accuracy of predicting distribution of user with certain contextual knowledge on a flight ticket order dataset.
\item We apply the predicting result in recommendation, and the result shows that our approach can effectively improve the accuracy.
\end{enumerate}
\textbf{Paper organization.} The rest of paper is structured as follows. We introduce related work in section 2. In section 3, we define the problem and describe the model, besides we show part of process on parameter inference. In section 4, we present dataset, evaluating metric and the result of predicting and recommendation. Finally, we conclude the paper in section 5.

\section{Related Work}
\textbf{Content based recommendation.} In online travel agency fields such as airline tickets or hotel booking, the items are usually highly structured, however, the content of items are quite mutable. Thus we can't propose a general metric to define items. Content-based recommender systems \cite{tech:cset}\cite{lops:handbook}are appropriate for highly structured items. The method needs proper measurements for representing the attributes of items and the profile of user interests, then it matches up the profile of user's interest with attributes of items. In general, a content-based recommender systems consists of three components. Content analyzer extract the structured attributes of items through a series of pre-processing steps. It produces the input for the system, which always needs domain related knowledge. The profile learner analyzes and constructs user's profile of interests by collected user's history behaviors. In addition, this component also relies on feedbacks of users. The filtering component evaluate the relevance of items for particular user through matching them with user's profile. The output for an item can be either binary or continuous, in this stage, some similarity measurements including cosine or euclidean distance can usually be applied.\par
\textbf{Implicit feedback.} Learning a profile of user interests is a form of classification. The training data is labeled user history behavior log. Typically, for explicit feedback, training data can be divided into binary classes, indicating whether the user likes the item or not. The explicit feedback can be acquired by ratings and text comments. However, explicit feedback increases the cognitive load on user, so users may not willing to provide feedback, and it also suffers from the transformation of user interests. In several application domains, a single numeric rating may not be adequate for describing users feeling over an item. Implicit feedback methods\cite{song:mining} are based on assigning a relevance score to specific actions on an item, such as clicking ,collecting, bookmarking, etc. These actions do not require user's involvement directly, so it also has the advantage of being free from the problem of lacking feedback data. Nevertheless, implicit feedback methods suffer from lacking of negative feedbacks and data noises. Based on the weakness of implicit feedback recommender systems, some methods are proposed, such as one class collaborative filtering and content based recommender.\par
\textbf{Probabilistic topic models.} Some information retrieval approaches are involved in  model based recommender systems. Topic models\cite{blei:lda}\cite{mic:atm}\cite{mark:prob} are proposed for automated extraction of useful semantic information from corpus data, which are widely used in information retrieval, document annotation, etc. The main process of models are extracting latent factors from corpus, named topics, which are commonly probabilistic distribution over words. Topic models have three major advantages over other document modeling methods. At first, topic models provide a completely unsupervised approach to extracting topics, thus requiring no document labels and no initialization. Unsupervised methods are necessary for modeling large document corpus, besides, in some fields, with the rapid change of content's topics, predefined topic categories may not reflect the development of specific field. Secondly, latent topics are interpretable respectively, so that extracted results are understandable for users. Finally, each document may consist of multiple topics, document can be considered as probabilistic distribution over topics. Many existing models regard documents as mixtures of topics, such as pLSI, LDA. The author topic model is a generative model that extends LDA to include authorship information for document modeling.\par
\textbf{Shared account recommendation.} Some work aims at addressing the challenge of multiple user sharing a single account. A top-N recommendation for shared accounts approach was proposed by Koen et al.\cite{koen:top-n} It is an item-based top-N collaborative filtering recommender system on binary, positive-only feedback. Another method proposed by Santosh et al.\cite{kabbur:nlmf} models users within an account with a much richer representation. It uses a nonlinear matrix factorization methods for predicting the recommendation score. Yutaka et al.\cite{yutaka:modeling} introduced an approach for modeling multiple users' purchase in a single account using an extended pLSA model. All above methods are applied in scenario that users' personal information can't be acquired precisely.

\section{User Prediction Model}
In this section, we propose a generic model for predict the probabilistic distribution of users within an account and produce the prediction result under certain contextual environment. Finally we integrate user prediction process into recommendation to get a better recommendation. Figure 2 shows an overview of the recommendation process. At first,a dataset for account orders are stored, each account may contains several users, whose identification can be acquired. We use this data to train user prediction model as well as extract preference at user granularity. Before a recommendation process starts, we calculate user distribution probability applying trained model and contextual knowledge of current session. At the final step, we generate a ranked candidate list as the recommendation result based on user prediction result and user's preference.\par
\begin{figure}[!hbt]
\centering
\includegraphics[scale=.40]{overview.eps}
\caption{Overview of user prediction integrated recommendation}
\label{fig:Prob}
\end{figure}\par

\subsection{Model description and notation}
Topic models are widely used in recommender systems. For example, in pLSA model\cite{tomas:coll}, a topic is a multinomial distribution over items, it represents the latent feature. And an account is a multinomial distribution over topics, it represents the preference of an account. For every purchase, we sample a topic z from account a, and take an item from topic z. Model-based recommender algorithms can usually achieve a higher prediction accuracy and reduce dimension of the dataset, in the meanwhile, it has more generality and flexibility.\par
In flight ticket booking field, the concept of item is quite different. Conventional items only have static features, means that the content of an item is less likely to change in the future. For flight tickets, however, the price changes frequently even for the same flight number and class. It is well known that the price factor plays a significant role in users' choice, so we can't consider the ticket of different price as one item. Besides, the amount of tickets for a flight is very limited, which leads to a very sparse user-item matrix, so we can't use a collaborative-filtering like method.\par
Fortunately, the decisive factors of a flight ticket are quite fixed, such as airline, takeoff time, price and class etc. Some factors are discrete while others are continuous. For continuous factors, we try to partition them into discrete non-overlapping intervals. Thus, the number of discrete alternatives of each factor is also very limited. We take orders within each account as a corpus. Our notations are summarized in table 1.\par
\begin{table}[!htbp]
\centering
\caption{Notation}
\begin{tabular}{|c|c|} \hline
$M$ & number of accounts within dataset\\ \hline
$V$ & number of words in vocabulary\\ \hline
$O$ & orders in an account\\ \hline
$P$ & passengers in an account\\ \hline
$P_i$ & passengers for order $O_i$ \\ \hline
$F$ & selected Factors\\ \hline
$V$ & size of vocabulary\\ \hline
$K$ & number of topics\\ \hline
\end{tabular}
\end{table}

In author topic model\cite{deiv:corpora}, a predefined vocabulary is generated containing discrete alternatives and intervals of all selected factors, we use integers to donate each entry in vocabulary. The model discovers both topics distributed in an order and passengers associated with distribution of topics. We treat every order as a bag of words, thus deduces each order to a vector of word counts. An order can be considered as a document with fixed word length, which can be represented as a vector of integers. All passengers corresponding to an order are co-authors for that document. Each passenger is associated with a multinomial distribution over topics and each topic is associated with a multinomial distribution over entries. The model essentially reduces dimension of documents, depending on the amount of topics.\par
For an account M, we generate the observed passenger list $P$. We denote authors' distribution over topics by a $|P| \times K$ matrix $\Theta$. The multinomial distribution can be generated from Dirichlet prior distribution with hyper-parameter $\alpha$. Topics' distribution over words is denoted by a $K \times \sum_{i=1}^{|F|}|F_i| $  matrix $\Phi$, also, distribution can be generated with hyper-parameter $\beta$. Generally, these hyper-parameters needn't be estimated, here, we fix $\alpha$ and $\beta$ at 50/K and 0.01 respectively. \par
To generate a word, we need draw two latent variables, respectively a passenger and a topic. First we draw a passenger uniformly from $P$, then a topic $Z$ from $\Theta_A$ and a word w from $\Phi_Z$. The following process describes generative model mathematically.\par

\begin{enumerate}
\item For each passenger $p=1,\dots,|P|$ draw $\Theta_p \sim Dirichlet(\alpha)$
\item For each topic $t=1,\dots,K$ draw $\Phi_t \sim Dirichlet(\beta)$
\item For each order $o=1,\dots,O$
       \begin{enumerate}[fullwidth,itemindent=1em,label=(\alph*)]
       \item given passengers $P$
       \item For each word $i=1,\dots, N_o$
              \begin{enumerate}[fullwidth,itemindent=2em,label=(\roman*)]
              \item draw a passenger $X_{oi} \sim Uniform(P)$
              \item draw a topic $Z_{oi} \sim Discrete(\theta_{X_{oi}})$
              \item draw a word $w_{oi} \sim Discrete(\phi_{Z_{oi}})$
              \end{enumerate}
       \end{enumerate}
\end{enumerate}
\begin{figure}[!hbt]
\centering
\includegraphics[scale=.55]{f1.eps}
\caption{Probability Graph for author topic model}
\label{fig:Prob}
\end{figure}\par
Figure 3 shows the graphical model corresponding to this process, where shaded and non-shaded nodes represent observed and unobserved variables respectively. It's a plate notation, the number at the bottom of each box indicates repeated time of operation. Arrows represents the conditional dependency between variables. In author topic model, observed variables includes words in an order and the passengers of the order.

\subsection{Parameter inference}
As mentioned above, the author topic model includes two sets of unknown parameters, the $P$ passenger-topic distributions $\theta$, and the $K$ topic-word distributions $\phi$. There are a variety of algorithms that can be applied to estimate the parameters of author topic models. The Expectation-Maximization algorithm and Gibbs sampling\cite{gregor:esti}. Generic EM algorithms are likely to face local maxima and computational inefficient. In this paper, we utilize Gibbs sampling, it does not explicitly estimate parameters, instead, it evaluates posteriori distribution just on drawn passenger $X$ and topic $Z$. Thus it is simple for Dirichlet priors.\par
We can obtain the probability of every word $\mathbf{w}_o$ generated in each order, conditioned on $\Theta$ and $\Phi$ is:\\
\begin{flalign}
\begin{split}
& P(\mathbf{w}_o | \Theta,\Phi,P) =\prod_{i=1}^{N_o}P(w_{oi}|\Theta,\Phi,\mathbf{p}_o) \\
& =\prod_{i=1}^{N_o}\sum_{p=1}^{|P|}\sum_{t=1}^{K}P(w_{oi}|z_{oi}=t,\Phi)
P(z_{oi}=t|x_{oi}=p,\Theta)P(x_{oi}=p|\mathbf{p}_o)\\
& =\prod_{i=1}^{N_o}\frac{1}{|P|}\sum_{p \in p_o}\sum_{t=1}^{K}\phi_{w_{oi}t}\theta_{tp}
\end{split} &
\end{flalign}

With the above generative model, $P(x_{oi}=p|\mathbf{p}_o)$ is assumed to be a uniform distribution over passenger list $P$. Each topic is drawn independently when conditioned on $\Theta$ and $p_o$, and each word is drawn independently when conditioned on $\Phi$ and $z$. Equation 1 can be applied as the likelihood of all orders in a single account. If we treat $\Theta$ and $\Phi$ as random variables, our target is to estimate the Maximum A Posteriori for the generative model.\par
In Gibbs sampling process, in order to draw a sample from the joint distribution $P(\mathbf{z},\mathbf{x}|\alpha,\beta)$, we need to draw the assignment of passenger $x_{di}$ and topic $z_{di}$ for a word $w_{di}$ conditioned on previous assignments for all other words in the whole corpus. In general, every word in the corpus should be sampled, and the batch sampling process will be performed for several iterations. Gregor\cite{gregor:esti} constructs a Markov chain that converges to the posteriori distribution on passenger $x$ and topic $z$. $p(\Theta,\Phi|\mathbf{z},\mathbf{x},\alpha,\beta)$ can be calculated by the property that Dirichlet distribution is conjugate to the multinomial distribution. Each pair of passenger and topic $(z_i,x_i)$ is drawn with the following equation:\\
\begin{flalign}
\begin{split}
& P(x_{oi}=p,z_{oi}=t|w_{oi}=w,\mathbf{z}_{-oi},\mathbf{x}_{-oi},\mathbf{w}_{-oi},\alpha,\beta,p_o)\\
&  \propto \frac{C_{tp}^{TP}+\alpha}{\sum{t'}C_{t'p}^{TP}+T\alpha}\frac{C_{wt}^{WT}+\beta}{\sum_{w'}C_{w't}^{WT}+W\beta}
\end{split} &
\end{flalign}\\
Equation 2 represents the probability of assigning topic t and passenger p for i-th word in order o. $C^{WT}$ is the word-topic matrix, and $C_{wt}$ is the number of times word $w$ is assigned to topic $t$ except for the current word. $C^{TP}$ represents the topic-passenger matrix, and $C_{tp}$ indicates the number of times passenger $p$ is assigned to topic $t$ except for the current word $w_{oi}$. $W$ is the size of vocabulary, $T$ represents the number of topics and $P$ is the number of passengers. From the sampling metric, we can estimate the topic-word distribution and passenger-topic distribution:\\
\begin{equation}
\theta_{tp} = \frac{C_{tp}^{TP}+\alpha}{\sum{t'}C_{t'p}^{TP}+T\alpha}
\end{equation}
\begin{equation}
\phi_{wt} = \frac{C_{wt}^{WT}+\beta}{\sum_{w'}C_{w't}^{WT}+W\beta}
\end{equation}\\
where $\theta_{tp}$ is the probability of drawing topic $t$ conditioned on passenger $p$ and $\phi_{wt}$ is the probability of drawing word $w$ conditioned on topic $t$. Thus in the process of parameter inference, we need to keep matrix $C^{TP}$ and $C^{WT}$, besides, the sampled word-topic list $T$ and sampled word-passenger list $P$ should be updated after each sample, where $T[o][i]$ represents the topic sampled for word i in order o, and $P[o][i]$ represents the passenger sampled.\par
The algorithm performs in three steps, respectively, initialization, sampling and updating. At the first step, we assign each word in corpus with random passengers and topics. Then for every topic $t$, we count the frequency of each vocabulary item assigned with $t$. For every passenger $p$, we count the frequency of each $K$ topic assigned with $p$. For every sampling operation, a word in corpus is chosen, the probability of topic distribution and passenger distribution is calculated conditioned on the rest words in corpus applying Equation 2, with these two probability, we can sample a new topic and passenger for the current word. After several batch iterations, the passenger-topic matrix $\Theta$ and topic-word matrix $\Phi$ can be updated applying Equation 3,4. So the computational efficiency is the number of words multiplies number of topics, passengers, and iteration times.\par
\subsection{Passengers Prediction}
Given the passenger topic probability matrix $\Theta$ and topic-word probability matrix $\Phi$. We can predict passengers for an anonymous order and a set of passengers. It's essentially a classification of an unlabeled order\cite{shanshan:unpopular}. We perform the classification by choosing the passengers who maximizes the probability $p(p|o_n)$, represented in the following equation:\\
\begin{equation}
p(x=p|o_n,\Theta,\Phi) \propto p(p)\prod_{w \in o_n}\sum_t p(t|w)p(w|t,p)
\end{equation}\\
where $p(p) = |O_p| / |O|$, $|O_p|$ is the number of orders participated by passenger p. $p(w|t,p) = p(t|p) \times p(w|t)$ since the process of drawing topic form a passenger and drawing word from a topic are independent from each other. $p(t|w)$ represents the probability that word w is assigned to topic t, which can be computed by $\frac{C^{wt}}{\sum_w'C^{w't}}$.\par
One important issue is how to determine the number of passengers. Through statistic analysis we find that most of test orders have exactly one passenger. In average, the probability of every passenger is $P_A = \frac{1}{|P|}$. We decide the passenger number by omitting passengers whose probability is not greater than $P_A$. We show the evaluation metric and prediction result in section 4.3.\par
%TODO:Conclude the algorithm
In conclusion, the passenger prediction task can be partitioned into two steps. For the first step, a set of decisive factors are extracted by domain field knowledge to generate a vocabulary. And the parameter $\Theta$ and $\Phi$ are trained through several batches of Gibbs sampling. In next step, passengers of an anonymous order can be predicted applying Equation 5. Algorithm 1 describes the predicting process mathematically.\par

\begin{algorithm}[htb]
\caption{passengerPrediction}
\label{alg0}
\begin{algorithmic}[1]
\REQUIRE
Account history order list $O$. \par
Predefined discrete factor list $F$ \par
A test anonymous order $o$
\ENSURE 
User's prediction list $Pl$
\STATE List $Pl \leftarrow \emptyset$;
\STATE stat word vector $\mathbf{W}$ for all orders;
\STATE Model $M \leftarrow trainATM(W)$;
\STATE calculate user's probability by Equation 5;
\FORALL{user : P}
\IF{$user.probability > \frac{1}{|P|}$}
\STATE $Pl.append(user,probability)$;
\ENDIF
\ENDFOR
\STATE normalize $Pl$;
\RETURN $Pl$;
\end{algorithmic} 
\end{algorithm}

\begin{algorithm}[htb]
\caption{trainATM}
\label{alg0}
\begin{algorithmic}[1]
\REQUIRE
Word vector $\overrightarrow{W}$. \par
A test anonymous order $to$
\ENSURE 
User-topic parameter $\Theta$ \par
Topic-word parameter $\Phi$
\STATE $nak , nkv, nak\_sum, nkv\_sum \leftarrow \mathbf{0}$
\FORALL{List o : $\overrightarrow{W}$}
\FORALL{Word w : o}
\STATE pick a topic $t$ and a user $p$ Multinomial;
\STATE user-topic count $nak[p][t] += 1$;
\STATE user-topic sum $nak\_sum[p] += 1$;
\STATE topic-word count $nkv[t][w] += 1$;
\STATE topic-word sum $nkv\_sum[t] += 1$;
\ENDFOR
\ENDFOR
\WHILE {not reach iteration limit}
\FORALL{List o : $\overrightarrow{W}$}
\FORALL{Word w : o}
\STATE $nak[p][t] -= 1, nak\_sum[p] -= 1$;
\STATE $nkv[t][w] -= 1, nkv\_sum[t] -= 1$;
\STATE sample a new user $p'$ and topic $t'$ by Equation 2;
\STATE $nak[p'][t'] += 1, nak\_sum[p'] += 1$;
\STATE $nkv[t'][w] += 1, nkv\_sum[t'] += 1$;
\ENDFOR
\ENDFOR
\ENDWHILE
\STATE calculate $\Theta,\Phi$ by Equation 3,4;
\RETURN $\Theta,\Phi$;
\end{algorithmic} 
\end{algorithm}

\section{Experiments}
In the following subsections, we introduce datasets, baseline method, evaluation metric. Then we evaluate the performance of user prediction and prediction integrated recommendation respectively.
\subsection{Dataset and baseline recommendation method}
In our experiments, we use a flight ticket dataset provided by Ctrip.com, consisting of all submitted orders for duration of two years. An order contains account id and all passengers' id. We use desensitized passenger id to distinguish individuals from each other. Besides, an order contains some travel information that can be considered as decisive factors, such as departure airport, arrival airport, order submitted time, takeoff time, etc. In our experiment, we sample several active users whose amount of history orders reaches a threshold, thus user's preference can be extracted with more confidence. In addition, many researches\cite{amy:guess}\cite{yutaka:modeling} on shared account recommendation generate an artificial dataset by composite single account. We also generate an artificial dataset combining single passengers from different accounts. We extract two passengers from arbitrary accounts and combine them as one account. If these passengers happen to take the same flight, we delete one order randomly. Overviews of two datasets and the meta data of orders are summarized in table 2 and table 3.
\begin{table}[!htbp]
\centering
\caption{Datasets}
\begin{tabular}{|c|c|c|c|} \hline
& \# accounts & \# passengers & \# orders\\ \hline
Real & 4632&7034&38907 \\ \hline
Artificial &1604&3208&29759\\ \hline
\end{tabular}
\end{table}

\begin{table}[!htbp]
\centering
\caption{Meta data}
\begin{tabular}{|c|c|} \hline
Travel Info & \tabincell{c}{airline, departure city, arrival city, \\departure airport, arrival airport, \\takeoff time, arrival time}\\ \hline
Content Info & \tabincell{c}{order time, login ip, geo location,\\ other trace log information}\\ \hline
Individual Info & account-id, passenger-id, age, gender\\ \hline
Order Info & \tabincell{c}{flight number, price , craft type, \\class, rescheduling/canceling policy}\\ \hline
\end{tabular}
\end{table}

The meta data of an order can be classified as travel information, context information, individual information and order information. Travel information contains the departure and arrival city, takeoff time. Context information contains time of browsing, other searching and filtering actions. Individual information contains account id, personal information. Order information consists of other content of an order.\par
%TODO: More concise method

With factors mentioned above, we propose a baseline content based recommendation method. First, select decisive factors and partition each factor as discrete variables or intervals, thus we can represent a candidate flight ticket as a vector. Then extract a user's preference from his history orders, for every factor, we generate a vector representing all alternatives and assign each dimension with the percentage of occurrence frequency. For every item in candidate ticket list, we compare it with users' preference model and get a score for every factor based on the frequency percentage. We can sum up score of every factor to get a total score for item, and rank all candidates in the list according to the total score. We can then provide a top-N recommendation.\par

In addition, different users may focus on different factors, thus we introduce a weight vector for every account. The evaluation of weight vector contains two steps, initializing and training, respectively. At initializing step, we estimate how much a user focuses on a factor through the information entropy, as mentioned in \cite{yang:pers}. We believe that if a user focuses on a factor, his behavior will be less random. The entropy $H$ is a measure to describe the uncertainty for discrete random variable $X$ and probability mass function $P(X)$. Here is the mathematical representation for entropy.\\
\begin{equation}
H(X)=E[-lnP(X)]= - \sum_{i-1}^n P(x_i)log_bP(X_i)
\end{equation}\par
The value b is the base of logarithm, and is usually 2. The entropy of every factor can be calculated and initialized as weight after normalization. Considering that different factors have a variety quantity of alternatives and the user may concern different factors some time later, we update the weight vector each time the user submits an order. For each submission, we have already produced a ranked list for recommendation, if the user doesn't choice top-N items, we consider this recommendation fails, so that the weight vector need be retrained to make the rank of selected item improved. The concept of weight training is mentioned in \cite{lor:flight}. By performing training weight for factors, we hope that the result of recommendation getting better in the future. The training procedure is quite straightforward. At first a learning rate should be defined, such as $\alpha = 0.1$ . If the selected item has lower similarity for factor f than items ranked before it, the weight of this factor should be shrunk. Otherwise, the weight should be enlarged. To avoid the problem of over-fitting, we define a max number of iteration step. So the stop criteria are either $1)$ the rank of selected items can't be improved anymore or $2$ the procedure reaches the iteration limit.\\
The baseline recommendation algorithm is described as Algorithm 3. First, extract a user's preference list $P$ and initialize weighted list $W$ through entropy. Items in candidate list are ranked based on inner product of $W$ and corresponding value of factor. After every recommendation, the list is retrained and stored depending on the item that user actually chose.

\begin{algorithm}[htb]
\caption{Baseline-Recommendation}
\label{alg1}
\begin{algorithmic}[1]
\REQUIRE
User's ID $u$ \par
User's history order list $O$ \par
Candidate item list $C$
\ENSURE Ranked candidate list $R$
\STATE Define a factor list $F$;
\STATE $P \leftarrow extractUserPref(O,F)$;
\STATE $W \leftarrow fetchWeightedList(u)$;
\IF{$W$ is $null$}
\STATE initialize $W$ by entropy;
\ENDIF
\STATE $R \leftarrow \emptyset$;
\FORALL { $c : C$} 
\STATE append $(c,weightedScore(c,W))$ to R;
\ENDFOR 
\STATE sort $R$ by score;
\STATE $trainWeightedList(W,R,P)$;
\STATE $saveWeightedList(u,W)$;
\RETURN $R$;
\end{algorithmic} 
\end{algorithm}

\begin{algorithm}[htb]
\caption{extractUserPref}
\label{alg2}
\begin{algorithmic}[1]
\REQUIRE
User's history order list $O$. \par
Predefined discrete factor list $F$
\ENSURE 
User's preference list $P$
\STATE List $P \leftarrow \emptyset$;
\FORALL {List $f : F$} 
\STATE append  $List(0,|f|)$  to $P$;
\ENDFOR
\FORALL{List $order : O$}
\FOR{$i: 1 \to |order| $}
\STATE $P[i][order_i] += 1$;
\ENDFOR	
\ENDFOR 
\RETURN $P$;
\end{algorithmic} 
\end{algorithm}

\begin{algorithm}[htb]
\caption{weightedScore}
\label{alg3}
\begin{algorithmic}[1]
\REQUIRE \par
Candidate item $c$ \par
User's preference list $P$ \par
User's weight vector $W$ 
\ENSURE Score of candidate $S$
\STATE $S \leftarrow 0$;
\FOR{$i: 1 \to |c| $}
\STATE $S += \frac{P[i][c_i]}{sum(P[i])} \times W[i]$;
\ENDFOR
\RETURN $S$;
\end{algorithmic} 
\end{algorithm}

\begin{algorithm}[htb]
\caption{trainWeightedList}
\label{alg4}
\begin{algorithmic}[1]
\REQUIRE \par
Ranked list $R$ \par
User's Preference list $P$ \par
User's weight list $W$ \par
User actually chose candidate $c$
\ENSURE Trained weighted list $W$
\STATE $R_c \leftarrow rankOf(R,c)$;
\STATE $\alpha \leftarrow 0.1$;
\STATE $count \leftarrow 0$;
\WHILE {$count < limit$}
\STATE $BeatList \leftarrow List(false,|W|)$;
\FOR{$i: 1 \to |W|$}
\FOR{$j: 1 \to R_c $}
\IF{$P[i][R_{ji}] > P[i][c_{i}] $}
\STATE $Beatlist[i] \leftarrow true$;
\STATE break;
\ENDIF
\ENDFOR
\IF{$BeatList[i] = true$}
\STATE $BeatList[i] \leftarrow false$;
\STATE $W[i] \leftarrow W[i] / (1+\alpha)$;
\ENDIF
\ENDFOR
\ENDWHILE
\STATE $normalize(W)$;
\RETURN $S$;
\end{algorithmic} 
\end{algorithm}

\subsection{Settings and Evaluation Metric}
Essentially, flight ticket recommendation is an approach to measure the similarity between candidates and user's preference. We take the latest order of one user as test data and the rest as training data. The test data also plays a role of providing contextual knowledge for user prediction.\par
One significant issue is that we can't reappear candidates at the time when user performed the search action. Fortunately, we can get an approximate set of candidate by collecting orders from all users in dataset with the same order date, takeoff date, departure city and arrival city as the test order, the granularity of the simulate candidate is to every flight, class and price range. Price range is a discrete interval representing the degree of the price based on domain knowledge. In order to get a persuasive evaluation result, we filter out test orders with the size of candidate list less than 20, and the average size of candidates is 45.\par
We apply two commonly used metrics MAP(Mean Average Precision) and top-N hit rate to evaluate the recommendation performance. The definition of MAP is described as follow:\\
\begin{equation}
MAP = \frac{\sum_{i=1}^{|M|}Acc(u_i)}{|M|}
\end{equation}

\begin{equation}
Acc(u_i) =
\begin{cases}
1 & \mbox{if N =1}\\
1 - \frac{index-1}{N-1} & \mbox{if N >1}
\end{cases}
\end{equation}

\begin{equation}
top-N = \frac{\sum_{i=1}^{|M|}|top-N(u_i) \cap O_{u_i}|}{|M|}
\end{equation}

where $|M|$ is the number of total test orders. $Acc(u_i)$ representing accuracy of recommendation base on the rank percentage of test order. The metric MAP is the average of each user's accuracy, and is a measurement for general performance. The top-N hit rate is the actual strategy for recommendation, we can stick up top-N candidates based on the ranked list. For each purchase, if top-N candidates hit the chosen order, we consider this recommendation has accuracy 1, else the accuracy is 0. We also calculate MAP for all accounts \par
For passenger prediction, we propose the following metric to evaluate the accuracy:\\
\begin{equation}
Acc(u_i) = \frac{P' \cap A}{\sqrt{|P'| \times |A|}}
\end{equation}\par
Since we treat one account as corpus, so a probabilistic distribution list is generated for all passengers contained in account. At first stage, we need to decide the passenger number of test order. Assuming that there are total $|P|$ passengers in an account. So in average case, the probability of every passenger is $P_A = \frac{1}{|P|}$. We decide the passenger number by omitting passengers whose probability is not greater than $P_A$. We denote predicted passenger list as $P'$, actual passenger list as $A$. Thus we can get the prediction accuracy in Equation 10. The numerator is the number of hit passengers, the denominator is penalty item for the size of predicted passenger list and predicted passenger list.

\subsection{Passenger Prediction}
We train a probabilistic model for every account where topics selected varying ${5,10,\dots,50}$. We take a test order for each account as a new document, then predict every passenger's probability for taking part in this order by Equation 5. According to above evaluating metric, the mean prediction accuracy rate of (a) real dataset and (b) artificial dataset is showed in Figure 4. The left sub-figure is the evaluating result for real dataset and the right one is for artificial dataset. The figure's horizontal axis shows the number of trained topics and the vertical axis shows the prediction accuracy computed by above mentioned metric. Baseline means assigning random probability to passengers, we also record $10$ batch of random results as our approach does. For artificial dataset, there are two passengers in every account and one passenger for every test order, so the accuracy of prediction is either 1.0 or 0. The result demonstrate that our model has a higher predicting precision than the baseline method on both dataset. We notice that the average improvement of prediction accuracy for artificial dataset is higher than real dataset. Besides, when the topic count is 10 or 15, both datasets get the best performance, the performance goes down with the topic size enlarging. The size of corpus' vocabulary and number of words in each order impact a lot on optimal topic size. In the next subsection, we evaluate the recommendation with topic size fixed at 10.\par 
%TODO figure 2

\begin{figure}[!h]
              \begin{minipage}[t]{0.47\linewidth}
              \centering
              \includegraphics[width=1.17\linewidth]{e5.eps}\\
              \label{Price_Distribution}
              \end{minipage}
              \begin{minipage}[t]{0.005\linewidth}~~~
              \end{minipage}
              \begin{minipage}[t]{0.47\linewidth}
              \centering
              \includegraphics[width=1.17\linewidth]{e6.eps}\\
              \label{Departure_Time_Distribution}
              \end{minipage}
              \begin{minipage}[t]{0.005\linewidth}~~~
              \end{minipage}
              \caption{MAP of user prediction}
          \label{total_rank}
          \vspace{-0.4cm}
\end{figure}

\subsection{Recommendation}
After get the predicted probabilistic distribution of passengers, we can extend content based recommendation approach by only extracting preference of predicted passengers. If there are multiple predicted passengers for one test order, we generate a composite preference model that combines all involved passenger's preference together. The probability of every passenger is normalized as weight.\par
The target of predicting passengers is to improve recommendation accuracy. We use MAP and top-N hit rate mentioned above to evaluate recommendation performance. We compare recommendation approaches including price rank, baseline content based recommendation and predicting content based recommendation. Price rank is a simple rank strategy that rank candidates by price in ascending order.\par

\begin{figure}[!h]
              \begin{minipage}[t]{0.47\linewidth}
              \centering
              \includegraphics[width=1.17\linewidth]{e1.eps}\\
              \label{Price_Distribution}
              \end{minipage}
              \begin{minipage}[t]{0.005\linewidth}~~~
              \end{minipage}
              \begin{minipage}[t]{0.47\linewidth}
              \centering
              \includegraphics[width=1.17\linewidth]{e2.eps}\\
              \label{Departure_Time_Distribution}
              \end{minipage}
              \begin{minipage}[t]{0.005\linewidth}~~~
              \end{minipage}
              \caption{top-N accuracy of recommendation}
          \label{total_rank}
          \vspace{-0.4cm}
\end{figure}
\begin{figure}[!h]
              \begin{minipage}[t]{0.47\linewidth}
              \centering
              \includegraphics[width=1.17\linewidth]{e3.eps}\\
              \label{Price_Distribution}
              \end{minipage}
              \begin{minipage}[t]{0.005\linewidth}~~~
              \end{minipage}
              \begin{minipage}[t]{0.47\linewidth}
              \centering
              \includegraphics[width=1.17\linewidth]{e4.eps}\\
              \label{Departure_Time_Distribution}
              \end{minipage}
              \begin{minipage}[t]{0.005\linewidth}~~~
              \end{minipage}
              \caption{MAP of recommendation}
          \label{total_rank}
          \vspace{-0.4cm}
\end{figure}\par
Figure 5 and 6 show recommendation accuracy for real dataset and artificial dataset respectively. The figure's horizontal axis shows the number of top-N recommended flights. The accuracy increases linearly with the growth of recommended flights. The result shows that the baseline recommendation approach performs much better than price rank strategy. And content based recommendation integrated with passengers prediction can achieve higher accuracy than baseline method. We have noticed the improvement in artificial dataset is larger than real dataset. The reason may be that passengers in artificial dataset have more difference between each other. In addition, passengers in the same account may book tickets for others at real data set, thus reducing the variety of passengers preference.

\section{Conclusion and future work}
In this paper, we proposed a generic probabilistic model to predict passengers in a single account based on passengers' history submitted orders. This model is appropriate for scenarios that individuals can be explicitly identified, such as in online travel agency service. For specified contextual environment, we can make a prediction for user distribution. Then we integrate user prediction into recommendation process. For experiment evaluation, we propose a general baseline content based recommendation approach for implicit feedback, and verify the efficiency of proposed model on two datasets. The result suggests that both passenger prediction and combined recommendation approach can get a higher accuracy. \par
In future work, we plan to do more research on how to determine the optimal amount of users in each session. We may learn and proposal a nonparametric Bayesian model. In addition, we may improve the approach to composite preference model of all predicted users. Thus make our model a wider range of recommender systems.

%
% The following two commands are all you need in the
% initial runs of your .tex file to
% produce the bibliography for the citations in your paper.
\bibliographystyle{abbrv}
\bibliography{sigproc}  % sigproc.bib is the name of the Bibliography in this case
% You must have a proper ".bib" file
%  and remember to run:
% latex bibtex latex latex
% to resolve all references
%
% ACM needs 'a single self-contained file'!

\end{document}

### 2016-06-28 Paper.tex
Add files via upload

@@
 % --- Author Metadata here ---
-\conferenceinfo{WOODSTOCK}{'97 El Paso, Texas USA}
+%\conferenceinfo{WOODSTOCK}{'97 El Paso, Texas USA}
 %\CopyrightYear{2007} % Allows default copyright year (20XX) to be over-ridden - IF NEED BE.
@@
 
-\title{A Context-Aware Method for User Prediction in Shared Accounts for Recommendation}
+\title{Passenger Prediction in Shared Accounts for Flight Ticket Recommendation}
 
@@
 \begin{abstract}
-Traditional recommender systems including collaborative filter and content-based method usually assume every account as a single user.
-However, under many circumstances, multiple users share a common account.
-Such as an online shopping account for family members and an online ticket booking account for family or companions.
-For the former case, service provider can't access user's personal information precisely.
-For the latter case, user's personal information can be acquired only after the user has submitted the order or checked in.
-If we can predict current user before he making a choice, then we may provide a more pertinent recommendation.
-For scenarios where user's within an account can't be identified precisely, there are some methods such as context aware methods and clustering.
-In this paper, we deal with the situation that user's personal information can be acquired.
-we propose a probabilistic method for user identification in a shared account with history behaviors and contextual knowledge.
-We then experimentally demonstrate its effectiveness on a dataset of Ctrip.com.
-The result show that our method outperforms conventional methods.
+Personalized recommendation is needed for online flight ticket booking service because it is a difficult task for a traveller to select the flight when the number of available flights is large.
+Traditionally, we can recommend flights for a user based on his historical orders from his account.
+However, people often book tickets for companions through his account.
+In this case, the preferences of other travellers should also be considered.
+Unfortuanately, before placing the order, people will not provider passengers' information.
+Therefore, we propose a probabilistic method for passenger prediction based on historical behaviors and contextual knowledge.
+We then experimentally demonstrate its effectiveness on a real dataset.
+The result shows that our method outperforms conventional methods.
 \end{abstract}
@@
 \section{Introduction}
-Recent years, with the repaid development of online travel agency, there are more and more passengers booking tickets or hotels through online service provider.
-It is quite common that a user books tickets for the whole family or companions.
-Typically, an user may input his location, destination and departure time, then he will get a list of candidate items.
-In general, there are dozens of items within a list , all of them are isomorphic.
-Thus, it takes quite long time for an user to compare and choose the most approximate one.
+Recent years, with the rapid development of online travel agency, there are more and more passengers booking flight tickets through online service providers.
+Typically, an user may input his location, destination and departure time, then he will get a list of candidate flights.
+In general, there are dozens of items within a list, all of them are isomorphic.
+Thus, it takes quite long time for the user to compare and choose the most appropriate one.
 Therefore, a recommender system is quite necessary to be applied for better user experience.
-Figure 1 shows a list for all candidate flights departure from Beijing to Hong Kong.
-There are total 156 matching flights in result.
+Figure 1 shows a list for all candidate flights departure from Beijing to Hong Kong when input a query.
+There are total 156 matchable flights in result.
 The website only provides simple sorting strategies such as departure time, arrival time, price.
@@
 Typical recommender systems assume that every account represents a single preference model.
-However, in many cases, multiple users will share one account.
-Depending on the service, some service providers can acquire user's personal information within an account precisely while others can't.
-For most online travel service providers, user's personal information can be acquired, for example, online airline ticket providers require users going aboard to fill in their personal information, and online hotel booking service providers can acquire users' personal information when they check in.
-It is likely that each user has different preference from each other.
-If we can identify users within a single account for current contextual environment, we may get the chance to improve accuracy of recommendation.\par
-To the best of our knowledge, all existing methods focus on extracting implicit users within an account.
-Some researches\cite{kabbur:nlmf}\cite{jason:embedding} extract users applying nonlinear latent factorization.
-Some researches\cite{koen:top-n}\cite{yutaka:modeling} focus on user extraction with no context information.
-These methods always treat an account as a fixed count of implicit users, and the experiment result can be only evaluated on artificial composite datasets.
-In this article, we deal with the challenge that service providers can acquire a user's personal information only after he has submitted the order.
-Our goal is to predict distribution of users in current session based on history behavior and contextual knowledge, thus we can make more pertinent recommendation.
-To achieve this target, we propose a probabilistic author topic model to analyze users' behavior.
-We regard all orders in an account as corpus, all users in account as authors, orders as documents, content attributes of the items and contextual knowledge as item list.
-Author is a multinomial distribution over topics and topic is a multinomial distribution over items.
-Note that if an order has more than one user, these users are co-authors of this document.\par
-In experiment section, we apply our method in a flight ticket order dataset of Ctrip, largest OTA service provider in China.
-In this dataset, we have submitted order as well as trace log in that session.
-And the result shows that our method has higher individual identification accuracy and a better recommendation accuracy.\par
-This article provides following contributions:\\
+However, in online flight ticket booking, it is quite common that a user books tickets for the whole family or companions.
+Obviously, every passenger has his own preferences.
+Unfortuanately, before placing the order, people will not provider passengers' information.
+Therefore, if we want to improve the accuracy of recommendation, we have to predict who are going to fly.
+\par
+To predict who is using the account to place orders is regarded as shared account problem.
+Some approaches have been proposed to extract implicit user information within an account.
+For example,  in \cite{kabbur:nlmf}\cite{jason:embedding} nonlinear latent factorization is applied to  extract user information.
+However, these methods only rely on the analysis of relationships between products and users \cite{koen:top-n}\cite{yutaka:modeling}, and context information that can help differentiate users is neglected.
+Besides, current methods always treat an account as a fixed number of implicit users, and the experiment result can be only evaluated on artificial composite datasets.
+The flight booking service providers can acquire user's personal information only after he has submitted the order.
+Thus, our goal is to predict distribution of passengers in current session based on historical behavior and contextual knowledge so that we can make more pertinent recommendations.
+To achieve this target, we adopt the probabilistic author topic model to analyze passengers' behaviors.
+We regard all orders in an account as corpus, all passengers appearing in the account as authors, orders as documents, content attributes of the items and contextual knowledge as item list.
+Note that if an order has more than one passenger, they are co-authors of this document.\par
+In experiment section, we apply our method to a real flight ticket order dataset.  And the result shows that our method has higher identification accuracy and a better recommendation accuracy.\par
+This paper has following contributions:\\
 \begin{enumerate}
-\item We provide a probabilistic user identification method for the situation, where personal information within an account can be acquired.
-\item We evaluate the accuracy of predicting distribution of user with certain contextual knowledge on a flight ticket order dataset.
-\item We apply the predicting result in recommendation, and the result shows that our approach can effectively improve the accuracy.
+\item We provide a probabilistic passenger identification method for online flight booking service.
+\item We apply the passenger prediction results to flight recommendation.
+\item We evaluate our approach on a real flight order dataset, and the result shows that our approach can effectively improve the recommendation accuracy.
 \end{enumerate}
 \textbf{Paper organization.} The rest of paper is structured as follows.
-We introduce related work in section 2.
-In section 3, we define the problem and describe the model, besides we show part of process on parameter inference.
-In section 4, we present dataset, evaluating metric and the result of predicting and recommendation.
+We introduce related work in Section 2.
+In Section 3, we define the problem and describe the model.
+Besides, we also discuss how to do parameter inference.
+In section 4, we introduce the experiment dataset, evaluation metrics and the experimental results of passenge prediction and flight recommendation.
 Finally, we conclude the paper in section 5.
@@
 \section{Related Work}
-\textbf{Content based recommendation.} In online travel agency fields such as airline tickets or hotel booking, the items are usually highly structured, however, the content of items are quite mutable.
-Thus we can't propose a general metric to define items.
+\textbf{Content based recommendation.} In online travel service industry such as airline tickets or hotel booking, the item information is usually highly structured, however, this information is quite mutable.
 Content-based recommender systems \cite{tech:cset}\cite{lops:handbook}are appropriate for highly structured items.
-The method needs proper measurements for representing the attributes of items and the profile of user interests, then it matches up the profile of user's interest with attributes of items.
-In general, a content-based recommender systems consists of three components.
-Content analyzer extract the structured attributes of items through a series of pre-processing steps.
-It produces the input for the system, which always needs domain related knowledge.
-The profile learner analyzes and constructs user's profile of interests by collected user's history behaviors.
+The method needs proper representations of the attributes of items and the profile of user interests, then it tries to match  the profile of user's interests with attributes of items.
+In general, a content-based recommender system consists of three components.
+A content analyzer extracts structured attributes of items through a series of pre-processing steps.
+It produces the inputs for the system, which always need domain related knowledge.
+A profile learner analyzes and constructs user's profile of interests by collecting user's historical behaviors.
 In addition, this component also relies on feedbacks of users.
-The filtering component evaluate the relevance of items for particular user through matching them with user's profile.
+A filtering component evaluates the relevance of items to particular users by matching them with users' profiles.
 The output for an item can be either binary or continuous, in this stage, some similarity measurements including cosine or euclidean distance can usually be applied.\par
-\textbf{Implicit feedback.} Learning a profile of user interests is a form of classification.
-The training data is labeled user history behavior log.
-Typically, for explicit feedback, training data can be divided into binary classes, indicating whether the user likes the item or not.
-The explicit feedback can be acquired by ratings and text comments.
-However, explicit feedback increases the cognitive load on user, so users may not willing to provide feedback, and it also suffers from the transformation of user interests.
-In several application domains, a single numeric rating may not be adequate for describing users feeling over an item.
-Implicit feedback methods\cite{song:mining} are based on assigning a relevance score to specific actions on an item, such as clicking ,collecting, bookmarking, etc.
-These actions do not require user's involvement directly, so it also has the advantage of being free from the problem of lacking feedback data.
-Nevertheless, implicit feedback methods suffer from lacking of negative feedbacks and data noises.
-Based on the weakness of implicit feedback recommender systems, some methods are proposed, such as one class collaborative filtering and content based recommender.\par
-\textbf{Probabilistic topic models.} Some information retrieval approaches are involved in  model based recommender systems.
-Topic models\cite{blei:lda}\cite{mic:atm}\cite{mark:prob} are proposed for automated extraction of useful semantic information from corpus data, which are widely used in information retrieval, document annotation, etc.
-The main process of models are extracting latent factors from corpus, named topics, which are commonly probabilistic distribution over words.
+
+\textbf{Flight Ticket Recommendation.} There is little work focusing on personalized flight ticket recommendation.
+Many online flight ticket booking agencies provide sorting, filtering strategies to improve user experience, such as sorting by price or takeoff time and filtering by airline or departure airport.
+Others also provide additional information that can help users, for example, placing the hottest flights at top or highlighting some of them.
+These methods do make sense in helping users find appropriate flights within less time.
+However, they can not provide personlized recommendations.
+In 2004, Lorcan Coyle\cite{lor:flight} proposed a Personal Travel Assistant(PTA).
+PTA is a method of case based reasoning, which takes user's historical orders as cases and recommends the most similar candidate flight to user's query.
+In addition, PTA also proposes attribute weight training and case storage method.\par
+\textbf{Implicit feedback.} The user's feedback can be divided into implict  or explict type.
+The explicit feedback can be acquired from users' ratings or text comments.
+However,  users may not willing to provide explict feedback since it needs additional efforts.
+Moreover, in many applications, a single numeric rating may not be adequate for describing users feeling to an item.
+Implicit feedback methods\cite{song:mining} try to infer users' attitudes to an item based on his behaviors, such as clicking ,collecting or bookmarking et al.
+It has the advantage of being free from the problem of lacking feedback data.
+Nevertheless, implicit feedback based recommender suffers from problems of lack of negative feedbacks and data noises.
+In order to provide recommendations when only implict feedbacks are available, some methods are proposed, such as one class collaborative filtering and content based recommender.\par
+\textbf{Probabilistic topic models.}  Topic models\cite{blei:lda}\cite{mic:atm}\cite{mark:prob} are proposed for automated extraction of useful semantic information from corpus data, which are widely used in information retrieval, document annotation, etc.
+The main step is extracting latent factors from corpus, named topics, which are commonly probabilistic distribution over words.
 Topic models have three major advantages over other document modeling methods.
-At first, topic models provide a completely unsupervised approach to extracting topics, thus requiring no document labels and no initialization.
+At first, topic models provide a completely unsupervised approach to extract topics, thus requiring no document labels and no initialization.
 Unsupervised methods are necessary for modeling large document corpus, besides, in some fields, with the rapid change of content's topics, predefined topic categories may not reflect the development of specific field.
@@
 Many existing models regard documents as mixtures of topics, such as pLSI, LDA.
-The author topic model is a generative model that extends LDA to include authorship information for document modeling.\par
-\textbf{Shared account recommendation.} Some work aims at addressing the challenge of multiple user sharing a single account.
+The author topic model is a generative model that extends LDA to include authorship information for document modeling.
+In our approach, topic model is innovatively applied to indentify users.
+\par
+\textbf{Shared account recommendation.} Some work aims at addressing the challenge of identifying current users who share a single account.
 A top-N recommendation for shared accounts approach was proposed by Koen et al.\cite{koen:top-n} It is an item-based top-N collaborative filtering recommender system on binary, positive-only feedback.
@@
 Yutaka et al.\cite{yutaka:modeling} introduced an approach for modeling multiple users' purchase in a single account using an extended pLSA model.
-All above methods are applied in scenario that users' personal information can't be acquired precisely.
+All above methods are applied in scenario that users' personal information can't be acquired explicitly.
 
-\section{User Prediction Model}
-In this section, we propose a generic model for predict the probabilistic distribution of users within an account and produce the prediction result under certain contextual environment.
-Finally we integrate user prediction process into recommendation to get a better recommendation.
+\section{Passenger Prediction Model}
+In this Section, we propose a generic model for predicting the probabilistic distribution of passengers under certain contextual environment.
+Finally we integrate user prediction into recommendation to get higher accuracy.
 Figure 2 shows an overview of the recommendation process.
-At first,a dataset for account orders are stored, each account may contains several users, whose identification can be acquired.
+At first,a dataset for orders are stored, each account may contains several passengers.
 We use this data to train user prediction model as well as extract preference at user granularity.
@@
 \includegraphics[scale=.40]{overview.eps}
-\caption{Overview of user prediction integrated recommendation}
+\caption{Overview of flight recommendation based on passenger prediction}
 \label{fig:Prob}
@@
 For example, in pLSA model\cite{tomas:coll}, a topic is a multinomial distribution over items, it represents the latent feature.
-And an account is a multinomial distribution over topics, it represents the preference of an account.
-For every purchase, we sample a topic z from account a, and take an item from topic z.
-Model-based recommender algorithms can usually achieve a higher prediction accuracy and reduce dimension of the dataset, in the meanwhile, it has more generality and flexibility.\par
-In flight ticket booking field, the concept of item is quite different.
+And an account is a multinomial distribution over topics, it can represent the preference of an account.
+Each purchase can be regared a sample that selects a topic z from account a, and takes an item from topic z.\par
+
+When topic model is applied to flight recommendation, there are some challenges.
+Firstly, the concepts behind flight tickets are quite different to be modeled.
 Conventional items only have static features, means that the content of an item is less likely to change in the future.
 For flight tickets, however, the price changes frequently even for the same flight number and class.
-It is well known that the price factor plays a significant role in users' choice, so we can't consider the ticket of different price as one item.
-Besides, the amount of tickets for a flight is very limited, which leads to a very sparse user-item matrix, so we can't use a collaborative-filtering like method.\par
+Since the price factor plays a significant role in users' choice, so we can't consider the ticket of different price as one item.
+Secondly, the amount of tickets for a flight is limited, which leads to a very sparse user-item matrix so that we can't use a collaborative-filtering like method directly.\par
+
 Fortunately, the decisive factors of a flight ticket are quite fixed, such as airline, takeoff time, price and class etc.
 Some factors are discrete while others are continuous.
-For continuous factors, we try to partition them into discrete non-overlapping intervals.
+For continuous factors, we can partition them into discrete non-overlapping intervals applying .
 Thus, the number of discrete alternatives of each factor is also very limited.
@@
 
-In author topic model\cite{deiv:corpora}, a predefined vocabulary is generated containing discrete alternatives and intervals of all selected factors, we use integers to donate each entry in vocabulary.
+In author-topic model\cite{deiv:corpora}, a predefined vocabulary is generated containing discrete alternatives and intervals of all selected factors, we use integers to donate each entry in vocabulary.
 The model discovers both topics distributed in an order and passengers associated with distribution of topics.
@@
 Each passenger is associated with a multinomial distribution over topics and each topic is associated with a multinomial distribution over entries.
-The model essentially reduces dimension of documents, depending on the amount of topics.\par
+The model essentially reduces dimensions of documents, depending on the amount of topics.\par
+
 For an account M, we generate the observed passenger list $P$.
@@
 \par
+
 To generate a word, we need draw two latent variables, respectively a passenger and a topic.
@@
 \includegraphics[scale=.55]{f1.eps}
-\caption{Probability Graph for author topic model}
+\caption{Probability Graph for the author-topic model}
 \label{fig:Prob}
@@
 Figure 3 shows the graphical model corresponding to this process, where shaded and non-shaded nodes represent observed and unobserved variables respectively.
-It's a plate notation, the number at the bottom of each box indicates repeated time of operation.
+It's a plate notation, the number at the bottom of each box indicates repeated times of operation.
 Arrows represents the conditional dependency between variables.
-In author topic model, observed variables includes words in an order and the passengers of the order.
+In the author-topic model, observed variables include words in an order and the passengers of the order.
 
 \subsection{Parameter inference}
-As mentioned above, the author topic model includes two sets of unknown parameters, the $P$ passenger-topic distributions $\theta$, and the $K$ topic-word distributions $\phi$.
-There are a variety of algorithms that can be applied to estimate the parameters of author topic models.
-The Expectation-Maximization algorithm and Gibbs sampling\cite{gregor:esti}.
+As mentioned above, the author-topic model includes two sets of unknown parameters, the $P$ passenger-topic distributions $\theta$, and the $K$ topic-word distributions $\phi$.
+There are a variety of algorithms that can be applied to estimate the parameters of author-topic models, the Expectation-Maximization algorithm and Gibbs sampling\cite{gregor:esti}.
 Generic EM algorithms are likely to face local maxima and computational inefficient.
@@
 So the computational efficiency is the number of words multiplies number of topics, passengers, and iteration times.\par
-\subsection{Passengers Prediction}
+\subsection{Passenger Prediction}
 Given the passenger topic probability matrix $\Theta$ and topic-word probability matrix $\Phi$.
@@
 We show the evaluation metric and prediction result in section 4.3.\par
-%TODO:Conclude the algorithm
 In conclusion, the passenger prediction task can be partitioned into two steps.
@@
 And the parameter $\Theta$ and $\Phi$ are trained through several batches of Gibbs sampling.
-In next step, passengers of an anonymous order can be predicted applying Equation 5.
+In the second step, passengers of an anonymous order can be predicted applying Equation 5.
 Algorithm 1 describes the predicting process mathematically.\par
@@
 \section{Experiments}
-In the following subsections, we introduce datasets, baseline method, evaluation metric. Then we evaluate the performance of user prediction and prediction integrated recommendation respectively.
-\subsection{Dataset and baseline recommendation method}
-In our experiments, we use a flight ticket dataset provided by Ctrip.com, consisting of all submitted orders for duration of two years.
+In the following subsections, we introduce datasets, preference-based recommendation method and evaluation metrics.
+Then we evaluate the performance of user prediction and passenger prediction based recommendation respectively.
+\subsection{Dataset and preference-based recommendation method}
+In our experiments, we use a real flight ticket dataset, consisting of all submitted orders for two years.
 An order contains account id and all passengers' id.
@@
 Besides, an order contains some travel information that can be considered as decisive factors, such as departure airport, arrival airport, order submitted time, takeoff time, etc.
-In our experiment, we sample several active users whose amount of history orders reaches a threshold, thus user's preference can be extracted with more confidence.
-In addition, many researches\cite{amy:guess}\cite{yutaka:modeling} on shared account recommendation generate an artificial dataset by composite single account.
+In our experiment, we select active users whose amount of history orders reaches a threshold, thus user's preference can be extracted with more confidence.
+In addition, many researches\cite{amy:guess}\cite{yutaka:modeling} on shared account recommendation generate an artificial dataset by compossing single accounts' data.
 We also generate an artificial dataset combining single passengers from different accounts.
 We extract two passengers from arbitrary accounts and combine them as one account.
-If these passengers happen to take the same flight, we delete one order randomly.
 Overviews of two datasets and the meta data of orders are summarized in table 2 and table 3.
@@
 
-The meta data of an order can be classified as travel information, context information, individual information and order information.
+The meta data of an order includes travel information, context information, individual information and order information.
 Travel information contains the departure and arrival city, takeoff time.
-Context information contains time of browsing, other searching and filtering actions.
+Context information contains time of browsing, searching and filtering actions.
 Individual information contains account id, personal information.
-Order information consists of other content of an order.\par
-%TODO: More concise method
+Order information consists of price, seat class, flight number, airline company  et al.\par
 
-With factors mentioned above, we propose a baseline content based recommendation method.
-First, select decisive factors and partition each factor as discrete variables or intervals, thus we can represent a candidate flight ticket as a vector.
-Then extract a user's preference from his history orders, for every factor, we generate a vector representing all alternatives and assign each dimension with the percentage of occurrence frequency.
+With factors mentioned above, we propose a user preference based recommendation method.
+First, select decisive factors and partition each factor's possible values to different levels, thus we can represent a candidate flight ticket as a vector.
+Then extract a user's preference from his historical orders, for every factor, we generate a vector representing all alternatives and assign each dimension with the percentage of occurrence frequency.
 For every item in candidate ticket list, we compare it with users' preference model and get a score for every factor based on the frequency percentage.
 We can sum up score of every factor to get a total score for item, and rank all candidates in the list according to the total score.
-We can then provide a top-N recommendation.\par
+We can then provide a top-$N$ recommendation.\par
 
-In addition, different users may focus on different factors, thus we introduce a weight vector for every account.
-The evaluation of weight vector contains two steps, initializing and training, respectively.
-At initializing step, we estimate how much a user focuses on a factor through the information entropy, as mentioned in \cite{yang:pers}.
+In addition, different users may cares different factors, thus we introduce a weight vector for every account.
+The evaluation of this weight vector contains two steps, initializing and training, respectively.
+At the initializing step, we estimate how much a user focuses on a factor through the information entropy, as mentioned in \cite{yang:pers}.
 We believe that if a user focuses on a factor, his behavior will be less random.
@@
 \end{equation}\par
-The value b is the base of logarithm, and is usually 2.
-The entropy of every factor can be calculated and initialized as weight after normalization.
-Considering that different factors have a variety quantity of alternatives and the user may concern different factors some time later, we update the weight vector each time the user submits an order.
-For each submission, we have already produced a ranked list for recommendation, if the user doesn't choice top-N items, we consider this recommendation fails, so that the weight vector need be retrained to make the rank of selected item improved.
+The value $b$ is the base of logarithm, and is usually 2.
+The entropy of every factor can be calculated and initialized as the weight value after normalization.
+Considering that different factors have a variety quantity of alternatives and the user may concern different factors some time later, we update the weight vector once the user submits an order.
+For each submission, we have already produced a ranked list for recommendations, if the user doesn't choice an item (i.e, a ticket) from top-$N$ items, we consider this recommendation fails, so that the weight vector need be retrained to make the rank of selected item improved.
 The concept of weight training is mentioned in \cite{lor:flight}.
-By performing training weight for factors, we hope that the result of recommendation getting better in the future.
+By performing weight training for factors, we hope that the result of recommendation getting better in the future.
 The training procedure is quite straightforward.
-At first a learning rate should be defined, such as $\alpha = 0.1$ .
-If the selected item has lower similarity for factor f than items ranked before it, the weight of this factor should be shrunk.
-Otherwise, the weight should be enlarged.
-To avoid the problem of over-fitting, we define a max number of iteration step.
-So the stop criteria are either $1)$ the rank of selected items can't be improved anymore or $2$ the procedure reaches the iteration limit.\\
-The baseline recommendation algorithm is described as Algorithm 3.
-First, extract a user's preference list $P$ and initialize weighted list $W$ through entropy.
+At first a learning rate should be set, such as $\alpha = 0.1$ .
+If the selected item has lower similarity for factor $f$ than items ranked before it, the weight value of this factor should be decreased.
+Otherwise, the weight value should be increased.
+To avoid the problem of over-fitting, we define a maximum number of iteration step.
+So the stop criteria is either $1)$ the rank of selected items can't be improved anymore or $2)$ the procedure reaches the iteration time limitation.\\
+The preference based recommendation algorithm is described as Algorithm 3.
+First extracting a user's preference  $P$ and initializing weighted list $W$ through entropy.
 Items in candidate list are ranked based on inner product of $W$ and corresponding value of factor.
-After every recommendation, the list is retrained and stored depending on the item that user actually chose.
+After every recommendation, the list is retrained and stored depending on the item that user actually chosen.
 
 \begin{algorithm}[htb]
-\caption{Baseline-Recommendation}
+\caption{Preference-Based-Recommendation}
 \label{alg1}
@@
 
-\subsection{Settings and Evaluation Metric}
-Essentially, flight ticket recommendation is an approach to measure the similarity between candidates and user's preference.
-We take the latest order of one user as test data and the rest as training data.
+\subsection{Settings and Evaluation Metrics}
+Essentially, flight ticket recommendation is an approach to select the best mached ticket by measuring the similarities between candidate tickets and user's preferences.
+We take the latest order of a user as the test data and the rest ones as the training data.
 The test data also plays a role of providing contextual knowledge for user prediction.\par
-One significant issue is that we can't reappear candidates at the time when user performed the search action.
+One significant issue is that we can't know real candidates at the time when user performed the search action.
 Fortunately, we can get an approximate set of candidate by collecting orders from all users in dataset with the same order date, takeoff date, departure city and arrival city as the test order, the granularity of the simulate candidate is to every flight, class and price range.
@@
 In order to get a persuasive evaluation result, we filter out test orders with the size of candidate list less than 20, and the average size of candidates is 45.\par
-We apply two commonly used metrics MAP(Mean Average Precision) and top-N hit rate to evaluate the recommendation performance. The definition of MAP is described as follow:\\
+We apply two commonly used metrics MAP(Mean Average Precision) and top-$N$ hit rate to evaluate the recommendation performance. The definition of MAP is described as follow:\\
 \begin{equation}
@@
 
-where $|M|$ is the number of total test orders.
-$Acc(u_i)$ representing accuracy of recommendation base on the rank percentage of test order.
+where $|M|$ is the number of total test orders, $Acc(u_i)$ represents the accuracy of recommendation based on the rank percentages of test orders.
 The metric MAP is the average of each user's accuracy, and is a measurement for general performance.
-The top-N hit rate is the actual strategy for recommendation, we can stick up top-N candidates based on the ranked list.
-For each purchase, if top-N candidates hit the chosen order, we consider this recommendation has accuracy 1, else the accuracy is 0.
+The top-$N$ hit rate is the actual strategy for recommendation, we can stick up top-$N$ candidates based on the ranked list.
+For each purchase, if top-$N$ candidates hit the chosen order, we consider this recommendation has accuracy 1, else the accuracy is 0.
 We also calculate MAP for all accounts \par
@@
 \end{equation}\par
-Since we treat one account as corpus, so a probabilistic distribution list is generated for all passengers contained in account.
-At first stage, we need to decide the passenger number of test order.
+Since we treat every account as a corpus, so a probabilistic distribution list is generated for all passengers contained in the account.
+At the first stage, we need to decide the passenger number for each test order.
 Assuming that there are total $|P|$ passengers in an account.
@@
 We denote predicted passenger list as $P'$, actual passenger list as $A$.
-Thus we can get the prediction accuracy in Equation 10.
-The numerator is the number of hit passengers, the denominator is penalty item for the size of predicted passenger list and predicted passenger list.
+Thus we can get the prediction accuracy by Equation 10.
+The numerator is the number of hitted passengers, the denominator is penalty item for the size of predicted passenger list and predicted passenger list.
 
 \subsection{Passenger Prediction}
-We train a probabilistic model for every account where topics selected varying ${5,10,\dots,50}$.
-We take a test order for each account as a new document, then predict every passenger's probability for taking part in this order by Equation 5.
-According to above evaluating metric, the mean prediction accuracy rate of (a) real dataset and (b) artificial dataset is showed in Figure 4.
-The left sub-figure is the evaluating result for real dataset and the right one is for artificial dataset.
-The figure's horizontal axis shows the number of trained topics and the vertical axis shows the prediction accuracy computed by above mentioned metric.
-Baseline means assigning random probability to passengers, we also record $10$ batch of random results as our approach does.
-For artificial dataset, there are two passengers in every account and one passenger for every test order, so the accuracy of prediction is either 1.0 or 0.
-The result demonstrate that our model has a higher predicting precision than the baseline method on both dataset.
-We notice that the average improvement of prediction accuracy for artificial dataset is higher than real dataset.
-Besides, when the topic count is 10 or 15, both datasets get the best performance, the performance goes down with the topic size enlarging.
-The size of corpus' vocabulary and number of words in each order impact a lot on optimal topic size.
-In the next subsection, we evaluate the recommendation with topic size fixed at 10.\par
-%TODO figure 2
+We train a probabilistic model for every account where topic number selected varying ${5,10,\dots,50}$.
+We pick a test order for each account as a new document, then predict every passenger's probability of placing this order by Equation 5.
+According to above evaluating metrics, the mean prediction accuracy rate of (a) real dataset and (b) artificial dataset is shown in Figure 4.
+The left sub-figure is the evaluation result on the real dataset and the right one is on the artificial dataset.
+The figure's horizontal axis shows the number of trained topics and the vertical axis shows the prediction accuracy computed by applying above mentioned metrics.
+The baseline means assigning random probabilities to passengers, we also record $10$ batch of random results as our approach does.
+For the artificial dataset, there are two passengers in every account and one passenger for every test order, so the accuracy of prediction is either 1.0 or 0.
+The results demonstrate that our model has a higher prediction precision than the baseline method on both datasets.
+We notice that the average improvements of prediction accuracy on artificial dataset is higher than on the real dataset.
+Besides, when the topic number is 10 or 15, both datasets get the best performance while the performance goes down with the topic number increasing.
+The sizes of corpus' vocabulary and number of words in each order also impact the optimal topic number.
+In the next subsection, we evaluate the recommendation performance with topic number fixed at 10.\par
 
@@
 \subsection{Recommendation}
-After get the predicted probabilistic distribution of passengers, we can extend content based recommendation approach by only extracting preference of predicted passengers.
-If there are multiple predicted passengers for one test order, we generate a composite preference model that combines all involved passenger's preference together.
-The probability of every passenger is normalized as weight.\par
-The target of predicting passengers is to improve recommendation accuracy.
-We use MAP and top-N hit rate mentioned above to evaluate recommendation performance.
-We compare recommendation approaches including price rank, baseline content based recommendation and predicting content based recommendation.
-Price rank is a simple rank strategy that rank candidates by price in ascending order.\par
+After obtaining the predicted probabilistic distribution of passengers, we can extend preference based recommendation approach by only extracting preferences of predicted passengers.
+If there are multiple predicted passengers for one test order, we generate a composite preference model that combines all involved passenger's preferences together.
+The probability of every passenger is normalized.\par
+We use MAP and top-$N$ hit rate mentioned above to evaluate recommendation performance.
+We compare different recommendation approaches including preference based recommendation, transfered preference based recommendation, price rank, hot rank and predicting preference based recommendation.
+The transfered preference based method is the same as the previous one except it takes the difference between flight distribution of various air routes into consideration.
+This method groups training data by route, and evaluates similarity between routes by flight distribution in some attributes such as airline, class, price range.
+If a user isn't active in target route, we transfer his preferences from most similar active routes with a transfer rate.
+In our experiment, the transfer rate is  $ \alpha = 0.5$.
+Price rank is a simple strategy that ranks candidates by price in an ascending order.
+Hot rank is a strategy that ranks candidates according to the hotness, which is based on the total order amount within a period of the previous two weeks, items are distinguished by flight number, class and price range.\par
 
@@
 Figure 5 and 6 show recommendation accuracy for real dataset and artificial dataset respectively.
-The figure's horizontal axis shows the number of top-N recommended flights.
+The figure's horizontal axis shows the number of top-$N$ recommended flights.
 The accuracy increases linearly with the growth of recommended flights.
 The result shows that the baseline recommendation approach performs much better than price rank strategy.
-And content based recommendation integrated with passengers prediction can achieve higher accuracy than baseline method.
+And content based recommendation combined with passenger prediction can achieve higher accuracy than baseline method.
 We have noticed the improvement in artificial dataset is larger than real dataset.
-The reason may be that passengers in artificial dataset have more difference between each other.
+The reason may be that passengers in artificial dataset have more difference preferences from each other.
 In addition, passengers in the same account may book tickets for others at real data set, thus reducing the variety of passengers preference.
@@
 \section{Conclusion and future work}
-In this paper, we proposed a generic probabilistic model to predict passengers in a single account based on passengers' history submitted orders.
-This model is appropriate for scenarios that individuals can be explicitly identified, such as in online travel agency service.
-For specified contextual environment, we can make a prediction for user distribution.
+In this paper, we proposed a generic probabilistic model to predict passengers in a single flight ticket booking account based on passengers' historical submitted orders.
+This model is also appropriate for scenarios that individuals can be explicitly identified, such as online hotel booking.
+For specified contextual environment, we can make a prediction for passenger distribution.
 Then we integrate user prediction into recommendation process.
-For experiment evaluation, we propose a general baseline content based recommendation approach for implicit feedback, and verify the efficiency of proposed model on two datasets.
-The result suggests that both passenger prediction and combined recommendation approach can get a higher accuracy.
+For experiment evaluation, we propose a general preference based recommendation approach for implicit feedback, and verify the efficiency of proposed model on two datasets.
+The results suggest that both passenger prediction and recommendation approach achieve a higher accuracy.
 \par
 In future work, we plan to do more research on how to determine the optimal amount of users in each session.
-We may learn and proposal a nonparametric Bayesian model.
-In addition, we may improve the approach to composite preference model of all predicted users.
-Thus make our model a wider range of recommender systems.
 

### 2016-06-28 Paper.tex
Add files via upload

@@
-% This is "sig-alternate.tex" V2.1 April 2013
-% This file should be compiled with V2.5 of "sig-alternate.cls" May 2012
-%
-% This example file demonstrates the use of the 'sig-alternate.cls'
-% V2.5 LaTeX2e document class file. It is for those submitting
-% articles to ACM Conference Proceedings WHO DO NOT WISH TO
-% STRICTLY ADHERE TO THE SIGS (PUBS-BOARD-ENDORSED) STYLE.
-% The 'sig-alternate.cls' file will produce a similar-looking,
-% albeit, 'tighter' paper resulting in, invariably, fewer pages.
-%
-% ----------------------------------------------------------------------------------------------------------------
-% This .tex file (and associated .cls V2.5) produces:
-%       1) The Permission STATEment
-%       2) The Conference (location) Info information
-%       3) The Copyright Line with ACM data
-%       4) NO page numbers
-%
-% as against the acm_proc_article-sp.cls file which
-% DOES NOT produce 1) thru' 3) above.
-%
-% Using 'sig-alternate.cls' you have control, however, from within
-% the source .tex file, over both the CopyrightYear
-% (defaulted to 200X) and the ACM Copyright Data
-% (defaulted to X-XXXXX-XX-X/XX/XX).
-% e.g.
-% \CopyrightYear{2007} will cause 2007 to appear in the copyright line.
-% \crdata{0-12345-67-8/90/12} will cause 0-12345-67-8/90/12 to appear in the copyright line.
-%
-% ---------------------------------------------------------------------------------------------------------------
-% This .tex source is an example which *does* use
-% the .bib file (from which the .bbl file % is produced).
-% REMEMBER HOWEVER: After having produced the .bbl file,
-% and prior to final submission, you *NEED* to 'insert'
-% your .bbl file into your source .tex file so as to provide
-% ONE 'self-contained' source file.
-%
-% ================= IF YOU HAVE QUESTIONS =======================
-% Questions regarding the SIGS styles, SIGS policies and
-% procedures, Conferences etc. should be sent to
-% Adrienne Griscti (griscti@acm.org)
-%
-% Technical questions _only_ to
-% Gerald Murray (murray@hq.acm.org)
-% ===============================================================
-%
-% For tracking purposes - this is V2.0 - May 2012
-
-\documentclass{sig-alternate-05-2015}
-
+\documentclass{llncs}
+\bibliographystyle{splncs}
 \usepackage{enumitem}
@@
 \usepackage{amsmath}
-\DeclareMathOperator*{\argmax}{arg\,max}
+\usepackage{graphicx}
+\usepackage[colorlinks,linkcolor=blue,anchorcolor=blue,citecolor=blue]{hyperref}
 \newcommand{\tabincell}[2]{\begin{tabular}{@{}#1@{}}#2\end{tabular}}
@@
 
-% Copyright
-\setcopyright{acmcopyright}
-%\setcopyright{acmlicensed}
-%\setcopyright{rightsretained}
-%\setcopyright{usgov}
-%\setcopyright{usgovmixed}
-%\setcopyright{cagov}
-%\setcopyright{cagovmixed}
-
-% DOI
-\doi{10.475/123_4}
-
-% ISBN
-\isbn{123-4567-24-567/08/06}
-
-%Conference
-\conferenceinfo{PLDI '13}{June 16--19, 2013, Seattle, WA, USA}
-
-\acmPrice{\$15.00}
-
-%
-% --- Author Metadata here ---
-%\conferenceinfo{WOODSTOCK}{'97 El Paso, Texas USA}
-%\CopyrightYear{2007} % Allows default copyright year (20XX) to be over-ridden - IF NEED BE.
-%\crdata{0-12345-67-8/90/01}  % Allows default copyright data (0-89791-88-6/97/05) to be over-ridden - IF NEED BE.
-% --- End of Author Metadata ---
-
 \title{Passenger Prediction in Shared Accounts for Flight Ticket Recommendation}
@@
 %
-% You need the command \numberofauthors to handle the 'placement
-% and alignment' of the authors beneath the title.
-%
-% For aesthetic reasons, we recommend 'three authors at a time'
-% i.e. three 'name/affiliation blocks' be placed beneath the title.
-%
-% NOTE: You are NOT restricted in how many 'rows' of
-% "name/affiliations" may appear. We just ask that you restrict
-% the number of 'columns' to three.
-%
-% Because of the available 'opening page real-eSTATE'
-% we ask you to refrain from putting more than six authors
-% (two rows with three columns) beneath the article title.
-% More than six makes the first-page appear very cluttered indeed.
-%
-% Use the \alignauthor commands to handle the names
-% and affiliations for an 'aesthetic maximum' of six authors.
-% Add names, affiliations, addresses for
-% the seventh etc. author(s) as the argument for the
-% \additionalauthors command.
-% These 'additional authors' will be output/set for you
-% without further effort on your part as the last section in
-% the body of your article BEFORE References or any Appendices.
 
-\numberofauthors{3} %  in this sample file, there are a *total*
-% of EIGHT authors. SIX appear on the 'first-page' (for formatting
-% reasons) and the remaining two appear in the \additionalauthors section.
-%
-\author{
-% You can go ahead and credit any number of authors here,
-% e.g. one 'row of three' or two rows (consisting of one row of three
-% and a second row of one, two or three).
-%
-% The command \alignauthor (no curly braces needed) should
-% precede each author name, affiliation/snail-mail address and
-% e-mail address. Additionally, tag each line of
-% affiliation/address with \affaddr, and tag the
-% e-mail address with \email.
-%
-% 1st. author
-\alignauthor
-XXX\\
-       \affaddr{XXX}\\
-       \affaddr{XX}\\
-       \email{XXX}
-% 2nd. author
-\alignauthor
-XXX\\
-       \affaddr{XXX}\\
-       \affaddr{XX}\\
-       \email{XXX}
-% 3rd. author
-\alignauthor
-XXX\\
-       \affaddr{XXX}\\
-       \affaddr{XX}\\
-       \email{XXX}
-}
-% There's nothing stopping you putting the seventh, eighth, etc.
-% author on the opening page (as the 'third row') but we ask,
-% for aesthetic reasons that you place these 'additional authors'
-% in the \additional authors block, viz.
-% Just remember to make sure that the TOTAL number of authors
-% is the number that will appear on the first page PLUS the
-% number that will appear in the \additionalauthors section.
+\author{Yafeng Zhao, Jian Cao}
+\institute{Department of Computer Science and Engineering,\\
+Shanghai Jiao Tong University, Shanghai 200240, China\\
+\email{zyfgs2012@163.com, cao-jian@sjtu.edu.cn}}
 
@@
 We then experimentally demonstrate its effectiveness on a real dataset.
-The result shows that our method outperforms conventional methods.
+The result shows that our method outperforms conventional methods.\\
+\keywords{recommender system, probabilistic topic model, shared account}
 \end{abstract}
 
-\keywords{recommender system, probabilistic topic model, shared account}
-
 \section{Introduction}
+\label{sec:intro}
 Recent years, with the rapid development of online travel agency, there are more and more passengers booking flight tickets through online service providers.
@@
 Therefore, a recommender system is quite necessary to be applied for better user experience.
-Figure 1 shows a list for all candidate flights departure from Beijing to Hong Kong when input a query.
+Figure \ref{fig:res} shows a list for all candidate flights departure from Beijing to Hong Kong when input a query.
 There are total 156 matchable flights in result.
 The website only provides simple sorting strategies such as departure time, arrival time, price.
-Thus, it may take quite long time for users to find the appropriate one.\par
+Thus, it may take quite long time for users to find the appropriate one.
 \begin{figure}[!hbt]
@@
 \caption{Search result for flight tickets}
-\label{fig:Prob}
+\label{fig:res}
 \end{figure}\par
@@
 \par
-To predict who is using the account to place orders is regarded as shared account problem.
+ +To predict who is using the account to place orders is regarded as shared account problem.
 Some approaches have been proposed to extract implicit user information within an account.
@@
 Besides, current methods always treat an account as a fixed number of implicit users, and the experiment result can be only evaluated on artificial composite datasets.
-The flight booking service providers can acquire user's personal information only after he has submitted the order.
+ +The flight booking service providers can acquire user's personal information only after he has submitted the order.
 Thus, our goal is to predict distribution of passengers in current session based on historical behavior and contextual knowledge so that we can make more pertinent recommendations.
@@
 Note that if an order has more than one passenger, they are co-authors of this document.\par
-In experiment section, we apply our method to a real flight ticket order dataset.  And the result shows that our method has higher identification accuracy and a better recommendation accuracy.\par
-This paper has following contributions:\\
+ +In experiment section, we apply our method to a real flight ticket order dataset.  And the result shows that our method has higher identification accuracy and a better recommendation accuracy.\par
+ +This paper has following contributions:\\
 \begin{enumerate}
-\item We provide a probabilistic passenger identification method for online flight booking service.
-\item We apply the passenger prediction results to flight recommendation.
-\item We evaluate our approach on a real flight order dataset, and the result shows that our approach can effectively improve the recommendation accuracy.
++\item We provide a probabilistic passenger identification method for online flight booking service.
++\item We apply the passenger prediction results to flight recommendation.
++\item We evaluate our approach on a real flight order dataset, and the result shows that our approach can effectively improve the recommendation accuracy.
 \end{enumerate}
+
 \textbf{Paper organization.} The rest of paper is structured as follows.
-We introduce related work in Section 2.
-In Section 3, we define the problem and describe the model.
+We introduce related work in Section \ref{sec:relw}.
+In Section \ref{sec:mod}, we define the problem and describe the model.
 Besides, we also discuss how to do parameter inference.
-In section 4, we introduce the experiment dataset, evaluation metrics and the experimental results of passenge prediction and flight recommendation.
-Finally, we conclude the paper in section 5.
+In section \ref{sec:exp}, we introduce the experiment dataset, evaluation metrics and the experimental results of passenge prediction and flight recommendation.
+Finally, we conclude the paper in section \ref{sec:con}.
 
 \section{Related Work}
+\label{sec:relw}
 \textbf{Content based recommendation.} In online travel service industry such as airline tickets or hotel booking, the item information is usually highly structured, however, this information is quite mutable.
@@
 The output for an item can be either binary or continuous, in this stage, some similarity measurements including cosine or euclidean distance can usually be applied.\par
-
 \textbf{Flight Ticket Recommendation.} There is little work focusing on personalized flight ticket recommendation.
@@
 In order to provide recommendations when only implict feedbacks are available, some methods are proposed, such as one class collaborative filtering and content based recommender.\par
+
 \textbf{Probabilistic topic models.}  Topic models\cite{blei:lda}\cite{mic:atm}\cite{mark:prob} are proposed for automated extraction of useful semantic information from corpus data, which are widely used in information retrieval, document annotation, etc.
@@
 \par
+
 \textbf{Shared account recommendation.} Some work aims at addressing the challenge of identifying current users who share a single account.
@@
 
-\section{Passenger Prediction Model}
+\section{User Prediction Model}
+\label{sec:mod}
 In this Section, we propose a generic model for predicting the probabilistic distribution of passengers under certain contextual environment.
@@
 \caption{Overview of flight recommendation based on passenger prediction}
-\label{fig:Prob}
+\label{fig:over}
 \end{figure}\par
@@
 Each purchase can be regared a sample that selects a topic z from account a, and takes an item from topic z.\par
-
 When topic model is applied to flight recommendation, there are some challenges.
@@
 Secondly, the amount of tickets for a flight is limited, which leads to a very sparse user-item matrix so that we can't use a collaborative-filtering like method directly.\par
-
 Fortunately, the decisive factors of a flight ticket are quite fixed, such as airline, takeoff time, price and class etc.
@@
 We take orders within each account as a corpus.
-Our notations are summarized in table 1.\par
+Our notations are summarized in table \ref{tab:not}.\par
 \begin{table}[!htbp]
 \centering
-\caption{Notation}
+\caption{\label{tab:not}Notation}
 \begin{tabular}{|c|c|} \hline
@@
 \caption{Probability Graph for the author-topic model}
-\label{fig:Prob}
+\label{fig:mod}
 \end{figure}\par
-Figure 3 shows the graphical model corresponding to this process, where shaded and non-shaded nodes represent observed and unobserved variables respectively.
+Figure \ref{fig:mod} shows the graphical model corresponding to this process, where shaded and non-shaded nodes represent observed and unobserved variables respectively.
 It's a plate notation, the number at the bottom of each box indicates repeated times of operation.
@@
 \begin{split}
+\label{eq:1} 
 & P(\mathbf{w}_o | \Theta,\Phi,P) =\prod_{i=1}^{N_o}P(w_{oi}|\Theta,\Phi,\mathbf{p}_o) \\
@@
 Each topic is drawn independently when conditioned on $\Theta$ and $p_o$, and each word is drawn independently when conditioned on $\Phi$ and $z$.
-Equation 1 can be applied as the likelihood of all orders in a single account.
+Equation \ref{eq:1} can be applied as the likelihood of all orders in a single account.
 If we treat $\Theta$ and $\Phi$ as random variables, our target is to estimate the Maximum A Posteriori for the generative model.\par
@@
 \begin{split}
+\label{eq:2}
 & P(x_{oi}=p,z_{oi}=t|w_{oi}=w,\mathbf{z}_{-oi},\mathbf{x}_{-oi},\mathbf{w}_{-oi},\alpha,\beta,p_o)\\
@@
 \end{flalign}\\
-Equation 2 represents the probability of assigning topic t and passenger p for i-th word in order o.
+Equation \ref{eq:2} represents the probability of assigning topic t and passenger p for i-th word in order o.
 $C^{WT}$ is the word-topic matrix, and $C_{wt}$ is the number of times word $w$ is assigned to topic $t$ except for the current word.
@@
 \begin{equation}
+\label{eq:3}
 \theta_{tp} = \frac{C_{tp}^{TP}+\alpha}{\sum{t'}C_{t'p}^{TP}+T\alpha}
@@
 \begin{equation}
+\label{eq:4}
 \phi_{wt} = \frac{C_{wt}^{WT}+\beta}{\sum_{w'}C_{w't}^{WT}+W\beta}
@@
 For every passenger $p$, we count the frequency of each $K$ topic assigned with $p$.
-For every sampling operation, a word in corpus is chosen, the probability of topic distribution and passenger distribution is calculated conditioned on the rest words in corpus applying Equation 2, with these two probability, we can sample a new topic and passenger for the current word.
-After several batch iterations, the passenger-topic matrix $\Theta$ and topic-word matrix $\Phi$ can be updated applying Equation 3,4.
+For every sampling operation, a word in corpus is chosen, the probability of topic distribution and passenger distribution is calculated conditioned on the rest words in corpus applying Equation \ref{eq:2}, with these two probability, we can sample a new topic and passenger for the current word.
+After several batch iterations, the passenger-topic matrix $\Theta$ and topic-word matrix $\Phi$ can be updated applying Equation \ref{eq:3}, \ref{eq:4}.
 So the computational efficiency is the number of words multiplies number of topics, passengers, and iteration times.\par
@@
 \begin{equation}
+\label{eq:5}
 p(x=p|o_n,\Theta,\Phi) \propto p(p)\prod_{w \in o_n}\sum_t p(t|w)p(w|t,p)
@@
 And the parameter $\Theta$ and $\Phi$ are trained through several batches of Gibbs sampling.
-In the second step, passengers of an anonymous order can be predicted applying Equation 5.
-Algorithm 1 describes the predicting process mathematically.\par
+In the second step, passengers of an anonymous order can be predicted applying Equation \ref{eq:5}.
+Algorithm \ref{alg:1} describes the predicting process mathematically.\par
 
@@
 \caption{passengerPrediction}
-\label{alg0}
 \begin{algorithmic}[1]
+\label{alg:1}
 \REQUIRE
@@
 \STATE Model $M \leftarrow trainATM(W)$;
-\STATE calculate user's probability by Equation 5;
+\STATE calculate user's probability by Equation \ref{eq:5};
 \FORALL{user : P}
@@
 \caption{trainATM}
-\label{alg0}
 \begin{algorithmic}[1]
+\label{alg:2}
 \REQUIRE
@@
 \STATE $nkv[t][w] -= 1, nkv\_sum[t] -= 1$;
-\STATE sample a new user $p'$ and topic $t'$ by Equation 2;
+\STATE sample a new user $p'$ and topic $t'$ by Equation \ref{eq:2};
 \STATE $nak[p'][t'] += 1, nak\_sum[p'] += 1$;
@@
 \ENDWHILE
-\STATE calculate $\Theta,\Phi$ by Equation 3,4;
+\STATE calculate $\Theta,\Phi$ by Equation \ref{eq:3} ,\ref{eq:4};
 \RETURN $\Theta,\Phi$;
@@
 \section{Experiments}
+\label{sec:exp}
 In the following subsections, we introduce datasets, preference-based recommendation method and evaluation metrics.
@@
 We extract two passengers from arbitrary accounts and combine them as one account.
-Overviews of two datasets and the meta data of orders are summarized in table 2 and table 3.
+Overviews of two datasets and the meta data of orders are summarized in table \ref{tab:dat} and table \ref{tab:mdat}.
 \begin{table}[!htbp]
 \centering
-\caption{Datasets}
+\caption{\label{tab:dat}Datasets}
 \begin{tabular}{|c|c|c|c|} \hline
@@
 \centering
-\caption{Meta data}
+\caption{\label{tab:mdat}Meta data}
 \begin{tabular}{|c|c|} \hline
@@
 So the stop criteria is either $1)$ the rank of selected items can't be improved anymore or $2)$ the procedure reaches the iteration time limitation.\\
-The preference based recommendation algorithm is described as Algorithm 3.
+ +The preference based recommendation algorithm is described as Algorithm \ref{alg:3}.
 First extracting a user's preference  $P$ and initializing weighted list $W$ through entropy.
@@
 \caption{Preference-Based-Recommendation}
-\label{alg1}
 \begin{algorithmic}[1]
+\label{alg:3}
 \REQUIRE
@@
 \caption{extractUserPref}
-\label{alg2}
 \begin{algorithmic}[1]
+\label{alg:4}
 \REQUIRE
@@
 \caption{weightedScore}
-\label{alg3}
 \begin{algorithmic}[1]
+\label{alg:5}
 \REQUIRE \par
@@
 \caption{trainWeightedList}
-\label{alg4}
 \begin{algorithmic}[1]
+\label{alg:6}
 \REQUIRE \par
@@
 \begin{equation}
+\label{eq:10}
 Acc(u_i) = \frac{P' \cap A}{\sqrt{|P'| \times |A|}}
@@
 We denote predicted passenger list as $P'$, actual passenger list as $A$.
-Thus we can get the prediction accuracy by Equation 10.
+Thus we can get the prediction accuracy by Equation \ref{eq:10}.
 The numerator is the number of hitted passengers, the denominator is penalty item for the size of predicted passenger list and predicted passenger list.
@@
 We train a probabilistic model for every account where topic number selected varying ${5,10,\dots,50}$.
-We pick a test order for each account as a new document, then predict every passenger's probability of placing this order by Equation 5.
-According to above evaluating metrics, the mean prediction accuracy rate of (a) real dataset and (b) artificial dataset is shown in Figure 4.
+We pick a test order for each account as a new document, then predict every passenger's probability of placing this order by Equation \ref{eq:5}.
+According to above evaluating metrics, the mean prediction accuracy rate of (a) real dataset and (b) artificial dataset is shown in Figure \ref{fig:pred}.
 The left sub-figure is the evaluation result on the real dataset and the right one is on the artificial dataset.
@@
               \includegraphics[width=1.17\linewidth]{e5.eps}\\
-              \label{Price_Distribution}
               \end{minipage}
@@
               \includegraphics[width=1.17\linewidth]{e6.eps}\\
-              \label{Departure_Time_Distribution}
               \end{minipage}
@@
               \caption{MAP of user prediction}
-          \label{total_rank}
-          \vspace{-0.4cm}
+          \label{fig:pred}
 \end{figure}
@@
 The probability of every passenger is normalized.\par
-We use MAP and top-$N$ hit rate mentioned above to evaluate recommendation performance.
+ +We use MAP and top-$N$ hit rate mentioned above to evaluate recommendation performance.
 We compare different recommendation approaches including preference based recommendation, transfered preference based recommendation, price rank, hot rank and predicting preference based recommendation.
@@
               \includegraphics[width=1.17\linewidth]{e1.eps}\\
-              \label{Price_Distribution}
               \end{minipage}
@@
               \includegraphics[width=1.17\linewidth]{e2.eps}\\
-              \label{Departure_Time_Distribution}
               \end{minipage}
@@
               \caption{top-N accuracy of recommendation}
-          \label{total_rank}
-          \vspace{-0.4cm}
+          \label{fig:top}
 \end{figure}
@@
               \includegraphics[width=1.17\linewidth]{e3.eps}\\
-              \label{Price_Distribution}
               \end{minipage}
@@
               \includegraphics[width=1.17\linewidth]{e4.eps}\\
-              \label{Departure_Time_Distribution}
               \end{minipage}
@@
               \caption{MAP of recommendation}
-          \label{total_rank}
-          \vspace{-0.4cm}
+          \label{fig:rank}
 \end{figure}\par
-Figure 5 and 6 show recommendation accuracy for real dataset and artificial dataset respectively.
+Figure \ref{fig:top} and \ref{fig:rank} show recommendation accuracy for real dataset and artificial dataset respectively.
 The figure's horizontal axis shows the number of top-$N$ recommended flights.
@@
 \section{Conclusion and future work}
+\label{sec:con}
 In this paper, we proposed a generic probabilistic model to predict passengers in a single flight ticket booking account based on passengers' historical submitted orders.
@@
 
-%
-% The following two commands are all you need in the
-% initial runs of your .tex file to
-% produce the bibliography for the citations in your paper.
-\bibliographystyle{abbrv}
-\bibliography{sigproc}  % sigproc.bib is the name of the Bibliography in this case
-% You must have a proper ".bib" file
-%  and remember to run:
-% latex bibtex latex latex
-% to resolve all references
-%
-% ACM needs 'a single self-contained file'!
+\begin{thebibliography}{1}
+\bibitem {koen:top-n}
+Koen,V.,Bart,G.:
+Top-N Recommendation for Shared Accounts.
+In: Proceedings of the 9th ACM Conference on Recommender Systems,59–66(2015)
+
+\bibitem {jason:embedding}
+Jason,W.,Ron,J.,Hector,Y.:
+Nonlinear Latent Factorization by Embedding Multiple User Interests.
+In: Proceedings of the 7th ACM Conference on Recommender Systems,65-68(2013)
+
+\bibitem {kabbur:nlmf}
+Santosh,K.,George,K.:
+NLMF: NonLinear Matrix Factorization Methods for Top-N Recommender Systems.
+In: International Conference on Data Mining Workshop,167-174(2014)
+
+\bibitem {amy:guess}
+Amy,Z.,Nadia,F.,Stratis,I.:
+Guess Who Rated This Movie: Identifying Users Through Subspace Clustering.
+In: Proceedings of Conference on Uncertainty in Artificial Intelligence,944-953(2012)
+
+\bibitem {yutaka:modeling}
+Yutaka,K.,Tomoharu,I.,Ko,F.:
+Modeling Multiple Users' Purchase over a Single Account for Collaborative Filtering.
+In: Proceedings of the 11th International Conference on WISE,328-341(2010)
+
+\bibitem {shanshan:unpopular}
+Shanshan,F.,Jian,C.,Yuwen,C.,Jing,Q.:
+A Model for Discovering Unpopular Research Interests.
+In: Proceedings of the 8th International Conference KSEM,382-393(2015)
+
+\bibitem {lops:handbook}
+Pasquale,L.,Marco,G.,Giovanni,S.:
+Content-based Recommender Systems: State of the Art and Trends.
+In: Recommender Systems Handbook,Springer US,73-105(2011)
+
+\bibitem {song:mining}
+Yan,S.,Ping,Y.,Chunhong,Z.,Yang J.:
+Implicit Feedback Mining for Recommendation.
+In: Proceedings of the First International Conference on Big Data Computing and Communication,373-385(2015)
+
+\bibitem {tech:cset}
+Deivendran,T.,B,S.:
+Content Based Recommender Systems.
+In: International Journal of Computer Science and Emerging Technologies,382-393(2011)
+
+\bibitem {blei:lda}
+DM,B.,AY,N.,MI,J.:
+Guess Who Rated This Movie: Identifying Users Through Subspace Clustering.
+In: Journal of Machine Learning Research,993-1022(2003)
+
+\bibitem {mic:atm}
+Michal,R.,Thomas,G.,Mark,S.,Padhraic,S.:
+The author-topic model for authors and documents.
+In: Proceedings of the 20th Conference on Uncertainty in Artificial Intelligence,487-494(2012)
+
+\bibitem {mark:prob}
+Mark,S.,Padhraic,S.,Michal,R.,Thomas,G.:
+Probabilistic Author topic Models for Information Discovery.
+In: Proceedings of ACM SigKDD conference knowledge discovery and data mining,306-315(2004)
+
+\bibitem {deiv:corpora}
+M,Rosen,Z.,Thomas,G.:
+Learning author-topic models from text corpora.
+In: ACM Transactions on Information Systems,312-324(2010)
+
+\bibitem {gregor:esti}
+Gregor,H.:
+Parameter Estimation for Text Analysis.
+University of Leipzig,Germany,2009
+
+\bibitem {lv:rec}
+Lu,L.,Matus,M.,Yeung,H.,Zhang,Y.:
+Recommender systems.
+Hangzhou Normal University,2012
+
+\bibitem {tomas:coll}
+Thomas,H.:
+Collaborative filtering via gaussian probabilistic latent semantic analysis.
+In: Proceedings of the 26th International ACM conference on Research and development in informaion retrieval,259-266(2004)
+
+\bibitem {lor:flight}
+Lorcan,C.:
+Making Personalised Flight Recommendations using Implicit Feedback.
+University of Dublin,2004
+
+\bibitem {yang:pers}
+Yang,F.:
+Personalized Flight Recommender.
+Shanghai Jiao Tong University,2016
+
+\end{thebibliography}
 

### 2016-06-28 Paper.tex
Add files via upload

@@
 \usepackage{graphicx}
+\usepackage{indentfirst}
 \usepackage[colorlinks,linkcolor=blue,anchorcolor=blue,citecolor=blue]{hyperref}
@@
 In this case, the preferences of other travellers should also be considered.
-Unfortuanately, before placing the order, people will not provider passengers' information.
+Unfortunately, before placing the order, people will not provider passengers' information.
 Therefore, we propose a probabilistic method for passenger prediction based on historical behaviors and contextual knowledge.
@@
 Obviously, every passenger has his own preferences.
-Unfortuanately, before placing the order, people will not provider passengers' information.
+Unfortunately, before placing the order, people will not provider passengers' information.
 Therefore, if we want to improve the accuracy of recommendation, we have to predict who are going to fly.
 \par
- +To predict who is using the account to place orders is regarded as shared account problem.
+ To predict who is using the account to place orders is regarded as shared account problem.
 Some approaches have been proposed to extract implicit user information within an account.
@@
 Besides, current methods always treat an account as a fixed number of implicit users, and the experiment result can be only evaluated on artificial composite datasets.
- +The flight booking service providers can acquire user's personal information only after he has submitted the order.
+ The flight booking service providers can acquire user's personal information only after he has submitted the order.
 Thus, our goal is to predict distribution of passengers in current session based on historical behavior and contextual knowledge so that we can make more pertinent recommendations.
@@
 Note that if an order has more than one passenger, they are co-authors of this document.\par
- +In experiment section, we apply our method to a real flight ticket order dataset.  And the result shows that our method has higher identification accuracy and a better recommendation accuracy.\par
- +This paper has following contributions:\\
+ In experiment section, we apply our method to a real flight ticket order dataset.  And the result shows that our method has higher identification accuracy and a better recommendation accuracy.\par
+ This paper has following contributions:\\
 \begin{enumerate}
-+\item We provide a probabilistic passenger identification method for online flight booking service.
-+\item We apply the passenger prediction results to flight recommendation.
-+\item We evaluate our approach on a real flight order dataset, and the result shows that our approach can effectively improve the recommendation accuracy.
+\item We provide a probabilistic passenger identification method for online flight booking service.
+\item We apply the passenger prediction results to flight recommendation.
+\item We evaluate our approach on a real flight order dataset, and the result shows that our approach can effectively improve the recommendation accuracy.
 \end{enumerate}
@@
 Besides, we also discuss how to do parameter inference.
-In section \ref{sec:exp}, we introduce the experiment dataset, evaluation metrics and the experimental results of passenge prediction and flight recommendation.
+In section \ref{sec:exp}, we introduce the experiment dataset, evaluation metrics and the experimental results of passenger prediction and flight recommendation.
 Finally, we conclude the paper in section \ref{sec:con}.
 
-\section{Related Work}
+\section{Related Work}\par
 \label{sec:relw}
@@
 These methods do make sense in helping users find appropriate flights within less time.
-However, they can not provide personlized recommendations.
+However, they can not provide personalized recommendations.
 In 2004, Lorcan Coyle\cite{lor:flight} proposed a Personal Travel Assistant(PTA).
@@
 In addition, PTA also proposes attribute weight training and case storage method.\par
-\textbf{Implicit feedback.} The user's feedback can be divided into implict  or explict type.
+\textbf{Implicit feedback.} The user's feedback can be divided into implicit  or explicit type.
 The explicit feedback can be acquired from users' ratings or text comments.
-However,  users may not willing to provide explict feedback since it needs additional efforts.
+However,  users may not willing to provide explicit feedback since it needs additional efforts.
 Moreover, in many applications, a single numeric rating may not be adequate for describing users feeling to an item.
@@
 Nevertheless, implicit feedback based recommender suffers from problems of lack of negative feedbacks and data noises.
-In order to provide recommendations when only implict feedbacks are available, some methods are proposed, such as one class collaborative filtering and content based recommender.\par
+In order to provide recommendations when only implicit feedbacks are available, some methods are proposed, such as one class collaborative filtering and content based recommender.\par
 
@@
 The author topic model is a generative model that extends LDA to include authorship information for document modeling.
-In our approach, topic model is innovatively applied to indentify users.
+In our approach, topic model is innovatively applied to identify users.
 \par
@@
 
-\section{User Prediction Model}
+\section{Passenger Prediction Model}
 \label{sec:mod}
@@
 And an account is a multinomial distribution over topics, it can represent the preference of an account.
-Each purchase can be regared a sample that selects a topic z from account a, and takes an item from topic z.\par
+Each purchase can be regarded a sample that selects a topic z from account a, and takes an item from topic z.\par
 When topic model is applied to flight recommendation, there are some challenges.
@@
 In our experiment, we select active users whose amount of history orders reaches a threshold, thus user's preference can be extracted with more confidence.
-In addition, many researches\cite{amy:guess}\cite{yutaka:modeling} on shared account recommendation generate an artificial dataset by compossing single accounts' data.
+In addition, many researches\cite{amy:guess}\cite{yutaka:modeling} on shared account recommendation generate an artificial dataset by composing single accounts' data.
 We also generate an artificial dataset combining single passengers from different accounts.
@@
 So the stop criteria is either $1)$ the rank of selected items can't be improved anymore or $2)$ the procedure reaches the iteration time limitation.\\
- +The preference based recommendation algorithm is described as Algorithm \ref{alg:3}.
+The preference based recommendation algorithm is described as Algorithm \ref{alg:3}.
 First extracting a user's preference  $P$ and initializing weighted list $W$ through entropy.
@@
 \subsection{Settings and Evaluation Metrics}
-Essentially, flight ticket recommendation is an approach to select the best mached ticket by measuring the similarities between candidate tickets and user's preferences.
+Essentially, flight ticket recommendation is an approach to select the best matched ticket by measuring the similarities between candidate tickets and user's preferences.
 We take the latest order of a user as the test data and the rest ones as the training data.
@@
 Thus we can get the prediction accuracy by Equation \ref{eq:10}.
-The numerator is the number of hitted passengers, the denominator is penalty item for the size of predicted passenger list and predicted passenger list.
+The numerator is the number of hit passengers, the denominator is penalty item for the size of predicted passenger list and predicted passenger list.
 
@@
 The figure's horizontal axis shows the number of trained topics and the vertical axis shows the prediction accuracy computed by applying above mentioned metrics.
-The baseline means assigning random probabilities to passengers, we also record $10$ batch of random results as our approach does.
+The Random method means assigning random probabilities to passengers, we also record $10$ batch of random results as our approach does.
 For the artificial dataset, there are two passengers in every account and one passenger for every test order, so the accuracy of prediction is either 1.0 or 0.
-The results demonstrate that our model has a higher prediction precision than the baseline method on both datasets.
+The results demonstrate that our model has a higher prediction precision than the random method on both datasets.
 We notice that the average improvements of prediction accuracy on artificial dataset is higher than on the real dataset.
@@
               \centering
-              \includegraphics[width=1.17\linewidth]{e5.eps}\\
+              \includegraphics[width=1.145\linewidth]{e5.eps}\\
               \end{minipage}
@@
               \centering
-              \includegraphics[width=1.17\linewidth]{e6.eps}\\
+              \includegraphics[width=1.145\linewidth]{e6.eps}\\
               \end{minipage}
@@
 The probability of every passenger is normalized.\par
- +We use MAP and top-$N$ hit rate mentioned above to evaluate recommendation performance.
-We compare different recommendation approaches including preference based recommendation, transfered preference based recommendation, price rank, hot rank and predicting preference based recommendation.
+We use MAP and top-$N$ hit rate mentioned above to evaluate recommendation performance.
+We compare different recommendation approaches including preference based recommendation(shorted as Pre), transfered preference based recommendation(tfPre), price rank(pRank), hot rank(hRank) and predicting preference based recommendation(pdPre).
 The transfered preference based method is the same as the previous one except it takes the difference between flight distribution of various air routes into consideration.
@@
               \centering
-              \includegraphics[width=1.17\linewidth]{e1.eps}\\
+              \includegraphics[width=1.145\linewidth]{e1.eps}\\
               \end{minipage}
@@
               \centering
-              \includegraphics[width=1.17\linewidth]{e2.eps}\\
+              \includegraphics[width=1.145\linewidth]{e2.eps}\\
               \end{minipage}
@@
               \centering
-              \includegraphics[width=1.17\linewidth]{e3.eps}\\
+              \includegraphics[width=1.145\linewidth]{e3.eps}\\
               \end{minipage}
@@
               \centering
-              \includegraphics[width=1.17\linewidth]{e4.eps}\\
+              \includegraphics[width=1.145\linewidth]{e4.eps}\\
               \end{minipage}

### 2016-06-28 Paper.tex
Add files via upload

@@
 Besides, we also discuss how to do parameter inference.
+In section \ref{sec:rec}, we propose a preference-based flight ticket recommendation approach, which also plays a role as a baseline method at evaluation stage.
 In section \ref{sec:exp}, we introduce the experiment dataset, evaluation metrics and the experimental results of passenger prediction and flight recommendation.
@@
 
-\section{Experiments}
-\label{sec:exp}
-In the following subsections, we introduce datasets, preference-based recommendation method and evaluation metrics.
-Then we evaluate the performance of user prediction and passenger prediction based recommendation respectively.
-\subsection{Dataset and preference-based recommendation method}
-In our experiments, we use a real flight ticket dataset, consisting of all submitted orders for two years.
-An order contains account id and all passengers' id.
-We use desensitized passenger id to distinguish individuals from each other.
-Besides, an order contains some travel information that can be considered as decisive factors, such as departure airport, arrival airport, order submitted time, takeoff time, etc.
-In our experiment, we select active users whose amount of history orders reaches a threshold, thus user's preference can be extracted with more confidence.
-In addition, many researches\cite{amy:guess}\cite{yutaka:modeling} on shared account recommendation generate an artificial dataset by composing single accounts' data.
-We also generate an artificial dataset combining single passengers from different accounts.
-We extract two passengers from arbitrary accounts and combine them as one account.
-Overviews of two datasets and the meta data of orders are summarized in table \ref{tab:dat} and table \ref{tab:mdat}.
-\begin{table}[!htbp]
-\centering
-\caption{\label{tab:dat}Datasets}
-\begin{tabular}{|c|c|c|c|} \hline
-& \# accounts & \# passengers & \# orders\\ \hline
-Real & 4632&7034&38907 \\ \hline
-Artificial &1604&3208&29759\\ \hline
-\end{tabular}
-\end{table}
+\section{The Preference-based recommendation approach}
+\label{sec:rec}
+Since there is little existing work aimed at flight ticket recommendation.
+In this section, we propose a user preference-based recommendation approach.
+In section \ref{sec:exp}, we will evaluate this method as well as some business ranking strategies, such as price rank etc, to demonstrate that this method has a better accuracy.
+Then, we will apply the passenger prediction results to improve recommendation accuracy further on.
 
-\begin{table}[!htbp]
-\centering
-\caption{\label{tab:mdat}Meta data}
-\begin{tabular}{|c|c|} \hline
-Travel Info & \tabincell{c}{airline, departure city, arrival city, \\departure airport, arrival airport, \\takeoff time, arrival time}\\ \hline
-Content Info & \tabincell{c}{order time, login ip, geo location,\\ other trace log information}\\ \hline
-Individual Info & account-id, passenger-id, age, gender\\ \hline
-Order Info & \tabincell{c}{flight number, price , craft type, \\class, rescheduling/canceling policy}\\ \hline
-\end{tabular}
-\end{table}
-
-The meta data of an order includes travel information, context information, individual information and order information.
-Travel information contains the departure and arrival city, takeoff time.
-Context information contains time of browsing, searching and filtering actions.
-Individual information contains account id, personal information.
-Order information consists of price, seat class, flight number, airline company  et al.\par
-
-With factors mentioned above, we propose a user preference based recommendation method.
-First, select decisive factors and partition each factor's possible values to different levels, thus we can represent a candidate flight ticket as a vector.
-Then extract a user's preference from his historical orders, for every factor, we generate a vector representing all alternatives and assign each dimension with the percentage of occurrence frequency.
-For every item in candidate ticket list, we compare it with users' preference model and get a score for every factor based on the frequency percentage.
-We can sum up score of every factor to get a total score for item, and rank all candidates in the list according to the total score.
-We can then provide a top-$N$ recommendation.\par
-
-In addition, different users may cares different factors, thus we introduce a weight vector for every account.
-The evaluation of this weight vector contains two steps, initializing and training, respectively.
+\subsection{Factor selection and frequency statistic}
+A flight ticket clearly contains a set of factors, such as price, takeoff time, craft size, etc.
+Thus some decisive factors should be chosen.
+Besides, these factors may be either discrete or continuous.
+We divide a continuous factor into a vector of intervals, so any factor can be represented as a vector of finite alternatives.
+Then, we analyze user's submitted orders by counting the frequency of all alternatives for each factor.
+In a word, a user's preference model can be described as a union of vectors, a vector indicates one factor and an element within one vector represents the frequency of corresponding alternative which the user has chosen.\par
+We can also represent a candidate flight ticket as a vector, where each element is the corresponding alternative of each factor.
+So, for every ticket in candidate list, we compare the vector with users' preference model and get a score for every factor based on the frequency.
+We can sum up score of every factor to get a total score for that item, and rank all candidates according to the total score.
+We can then generate a top-$N$ recommendation.\par
+\subsection{Weight of factors}
+Since users may care different factors, we introduce personalized weight vector for each user.
+The evaluation of this weight vector contains two steps, initializing and training.
 At the initializing step, we estimate how much a user focuses on a factor through the information entropy, as mentioned in \cite{yang:pers}.
-We believe that if a user focuses on a factor, his behavior will be less random.
+We believe that if a user focuses on a factor, his behavior will be more concentrated.
 The entropy $H$ is a measure to describe the uncertainty for discrete random variable $X$ and probability mass function $P(X)$.
@@
 Considering that different factors have a variety quantity of alternatives and the user may concern different factors some time later, we update the weight vector once the user submits an order.
-For each submission, we have already produced a ranked list for recommendations, if the user doesn't choice an item (i.e, a ticket) from top-$N$ items, we consider this recommendation fails, so that the weight vector need be retrained to make the rank of selected item improved.
+For each submission, we have already produced a ranked list for recommendations, if the user doesn't choose an item (i.e, a ticket) from top-$N$ items, we consider this recommendation fails, so that the weight vector need be retrained to make the rank of selected item improved.
 The concept of weight training is mentioned in \cite{lor:flight}.
@@
 \end{algorithm}
+
+\section{Experiments}
+\label{sec:exp}
+In the following subsections, we introduce datasets and evaluation metrics. Then we evaluate the performance of user prediction and passenger prediction based recommendation respectively.
+\subsection{Dataset}
+In our experiments, we use a real flight ticket dataset, consisting of all submitted orders for two years.
+An order contains account id and all passengers' id.
+We use desensitized passenger id to distinguish individuals from each other.
+Besides, an order contains some travel information that can be considered as decisive factors, such as departure airport, arrival airport, takeoff time, etc.
+In our experiment, we select active users whose amount of history orders reaches a threshold, thus user's preference can be extracted with more confidence.
+In addition, many researches\cite{amy:guess}\cite{yutaka:modeling} on shared account recommendation generate an artificial dataset by composing single accounts' data.
+We also generate an artificial dataset combining single passengers from different accounts.
+We extract two passengers from arbitrary accounts and combine them as one account.
+Overviews of two datasets and the meta data of orders are summarized in table \ref{tab:dat} and table \ref{tab:mdat}.
+\begin{table}[!htbp]
+\centering
+\caption{\label{tab:dat}Datasets}
+\begin{tabular}{|c|c|c|c|} \hline
+& \# accounts & \# passengers & \# orders\\ \hline
+Real & 4632&7034&38907 \\ \hline
+Artificial &1604&3208&29759\\ \hline
+\end{tabular}
+\end{table}
+
+\begin{table}[!htbp]
+\centering
+\caption{\label{tab:mdat}Meta data}
+\begin{tabular}{|c|c|} \hline
+Travel Info & \tabincell{c}{airline, departure city, arrival city, \\departure airport, arrival airport, \\takeoff time, arrival time}\\ \hline
+Content Info & \tabincell{c}{order time, login ip, geo location,\\ other trace log information}\\ \hline
+Individual Info & account-id, passenger-id, age, gender\\ \hline
+Order Info & \tabincell{c}{flight number, price , craft type, \\class, rescheduling/canceling policy}\\ \hline
+\end{tabular}
+\end{table}
+
+The meta data of an order includes travel information, context information, individual information and order information.
+Travel information contains the departure and arrival city, takeoff time.
+Context information contains time of browsing, searching and filtering actions.
+Individual information contains account id, personal information.
+Order information consists of price, seat class, flight number, airline company  et al.\par
 

### 2016-07-04 Paper.tex
Add files via upload

@@
 
-\title{Passenger Prediction in Shared Accounts for Flight Ticket Recommendation}
+\title{Passenger Prediction in Shared Accounts for Flight Service Recommendation}
 
@@
 \begin{abstract}
-Personalized recommendation is needed for online flight ticket booking service because it is a difficult task for a traveller to select the flight when the number of available flights is large.
-Traditionally, we can recommend flights for a user based on his historical orders from his account.
-However, people often book tickets for companions through his account.
+Personalized recommendation is needed for online flight booking service because it is a difficult task for a traveller to select the flight when the number of available flights is large.
+Traditionally, we can recommend flights to a user based on his historical orders collected from his account.
+However, people sometimes book tickets for his family members, friends or colleagues through his account.
 In this case, the preferences of other travellers should also be considered.
@@
 \label{sec:intro}
-Recent years, with the rapid development of online travel agency, there are more and more passengers booking flight tickets through online service providers.
-Typically, an user may input his location, destination and departure time, then he will get a list of candidate flights.
-In general, there are dozens of items within a list, all of them are isomorphic.
-Thus, it takes quite long time for the user to compare and choose the most appropriate one.
-Therefore, a recommender system is quite necessary to be applied for better user experience.
-Figure \ref{fig:res} shows a list for all candidate flights departure from Beijing to Hong Kong when input a query.
-There are total 156 matchable flights in result.
-The website only provides simple sorting strategies such as departure time, arrival time, price.
-Thus, it may take quite long time for users to find the appropriate one.
+Recent years, with the rapid development of online travel agencies, there are more and more passengers booking flights through online travel service providers.
+Typically, an user may input his departure city , arrival city  and departure time, then he will get a list of candidate flights.
+In general, there are dozens of flights within a list .
+Figure \ref{fig:res} shows a list for all candidate flights  from Beijing to Hong Kong when input a query.
+There are total 156 matchable flights and the website only provides simple sorting strategies such as departure time, arrival time or price.
+Thus, it may take quite a long time for users to find the appropriate one.
+Therefore, a recommender system is  necessary for better user experiences.
 \begin{figure}[!hbt]
@@
 \end{figure}\par
-Essentially, an item recommender system is used for generating a personalized ranking on a set of items\cite{lv:rec}.
-Typical recommender systems assume that every account represents a single preference model.
-However, in online flight ticket booking, it is quite common that a user books tickets for the whole family or companions.
-Obviously, every passenger has his own preferences.
+Essentially, a recommender system is used for generating a personalized ranking on a set of items\cite{lv:rec}.
+Typical recommender systems assume that the preference model of an individual can be learned from each account.
+However, for online flight booking, it is quite common that a user books flights for his family members, friends or colleagues.
+Obviously, every passenger has his own preferences, which should be considered in flight recommendation.
 Unfortunately, before placing the order, people will not provider passengers' information.
@@
 \par
- To predict who is using the account to place orders is regarded as shared account problem.
+ To predict who is using the account to place orders is regarded as the shared account problem.
 Some approaches have been proposed to extract implicit user information within an account.
-For example,  in \cite{kabbur:nlmf}\cite{jason:embedding} nonlinear latent factorization is applied to  extract user information.
-However, these methods only rely on the analysis of relationships between products and users \cite{koen:top-n}\cite{yutaka:modeling}, and context information that can help differentiate users is neglected.
-Besides, current methods always treat an account as a fixed number of implicit users, and the experiment result can be only evaluated on artificial composite datasets.
- The flight booking service providers can acquire user's personal information only after he has submitted the order.
-Thus, our goal is to predict distribution of passengers in current session based on historical behavior and contextual knowledge so that we can make more pertinent recommendations.
-To achieve this target, we adopt the probabilistic author topic model to analyze passengers' behaviors.
-We regard all orders in an account as corpus, all passengers appearing in the account as authors, orders as documents, content attributes of the items and contextual knowledge as item list.
-Note that if an order has more than one passenger, they are co-authors of this document.\par
- In experiment section, we apply our method to a real flight ticket order dataset.  And the result shows that our method has higher identification accuracy and a better recommendation accuracy.\par
+For example,  in \cite{kabbur:nlmf}\cite{jason:embedding} the nonlinear latent factorization is applied to  extract user information.
+However, these methods only rely on the analysis of relationships between products and users \cite{koen:top-n}\cite{yutaka:modeling}, and context information (such as time information, the query input) that can help differentiate users is neglected.
+Besides, current methods always assume an account represents a fixed number of implicit users, which are not always true in reality.
+Moreover, so far, the experiments have only been evaluated on artificial composite datasets.
+ The flight booking service providers can acquire passenger's personal information after he has submitted the order.
+Thus, our goal is to predict distributions of passengers in current session based on historical behaviors and contextual information so that we can make flight recommendations in a more precise way.
+To achieve this target, we adopt the probabilistic author-topic model to analyze passengers' behaviors.
+We regard all historical orders in an account as the corpus, all passengers appearing in the account as authors and orders together with context information as documents.
+Note that if an order has more than one passenger, they are regarded as co-authors of this document.\par
+ In experiment section, we apply our method to a real flight order dataset.  And the result shows that our method has higher identification accuracy and a better recommendation accuracy.\par
  This paper has following contributions:\\
@@
 Besides, we also discuss how to do parameter inference.
-In section \ref{sec:rec}, we propose a preference-based flight ticket recommendation approach, which also plays a role as a baseline method at evaluation stage.
-In section \ref{sec:exp}, we introduce the experiment dataset, evaluation metrics and the experimental results of passenger prediction and flight recommendation.
-Finally, we conclude the paper in section \ref{sec:con}.
+In Section \ref{sec:rec}, we propose a preference-based flight ticket recommendation approach, which also plays a role as a baseline method at evaluation stage.
+In Section \ref{sec:exp}, we introduce the experiment dataset, evaluation metrics, the experimental results of passenger prediction and flight recommendation.
+Finally, we conclude the paper in Section \ref{sec:con}.
 
@@
 \label{sec:relw}
-\textbf{Content based recommendation.} In online travel service industry such as airline tickets or hotel booking, the item information is usually highly structured, however, this information is quite mutable.
+\textbf{Content based Recommendation.} In online travel service industry such as airline tickets or hotel booking, the item (for example, an air ticket, a hotel booking order) information is usually highly structured, however, this information is quite mutable.
 Content-based recommender systems \cite{tech:cset}\cite{lops:handbook}are appropriate for highly structured items.
@@
 In general, a content-based recommender system consists of three components.
-A content analyzer extracts structured attributes of items through a series of pre-processing steps.
-It produces the inputs for the system, which always need domain related knowledge.
-A profile learner analyzes and constructs user's profile of interests by collecting user's historical behaviors.
+A content analyzer extracts structured attributes of items through a series of pre-processing steps and it produces the inputs for the system, which always needs domain related knowledge.
+A profile learner analyzes and constructs users' profiles of interests by collecting users' historical behaviors.
 In addition, this component also relies on feedbacks of users.
-A filtering component evaluates the relevance of items to particular users by matching them with users' profiles.
-The output for an item can be either binary or continuous, in this stage, some similarity measurements including cosine or euclidean distance can usually be applied.\par
-\textbf{Flight Ticket Recommendation.} There is little work focusing on personalized flight ticket recommendation.
-Many online flight ticket booking agencies provide sorting, filtering strategies to improve user experience, such as sorting by price or takeoff time and filtering by airline or departure airport.
-Others also provide additional information that can help users, for example, placing the hottest flights at top or highlighting some of them.
+A filtering component evaluates the relevances of items to particular users by matching them with users' profiles and the outputs can be either binary or continuous.
+In this stage, some similarity measurements including cosine or euclidean distance can usually be applied.\par
+\textbf{Flight Ticket Recommendation.} There is little work focusing on personalized flight  recommendations.
+Many online flight booking agencies provide sorting and filtering strategies to improve users' experiences, such as sorting by price or takeoff time and filtering by airline or departure city.
+Others also provide additional information that can help users, for example, placing the most popular flights at the top or highlighting some of them.
 These methods do make sense in helping users find appropriate flights within less time.
@@
 In 2004, Lorcan Coyle\cite{lor:flight} proposed a Personal Travel Assistant(PTA).
-PTA is a method of case based reasoning, which takes user's historical orders as cases and recommends the most similar candidate flight to user's query.
-In addition, PTA also proposes attribute weight training and case storage method.\par
-\textbf{Implicit feedback.} The user's feedback can be divided into implicit  or explicit type.
-The explicit feedback can be acquired from users' ratings or text comments.
-However,  users may not willing to provide explicit feedback since it needs additional efforts.
+PTA is based on case-based reasoning, which takes users' historical orders as cases and recommends the most similar candidate flights to users' queries.
+In addition, PTA also proposes the attribute weight training and case storage method.\par
+\textbf{Implicit Feedback.} The users' feedbacks can be divided into implicit or explicit type.
+The explicit feedbacks can be acquired from users' ratings or text comments.
+However,  users may not willing to provide explicit feedbacks since it needs additional efforts.
 Moreover, in many applications, a single numeric rating may not be adequate for describing users feeling to an item.
-Implicit feedback methods\cite{song:mining} try to infer users' attitudes to an item based on his behaviors, such as clicking ,collecting or bookmarking et al.
+Implicit feedback methods\cite{song:mining} try to infer users' attitudes to an item based on their behaviors, such as clicking, collecting or bookmarking et al.
 It has the advantage of being free from the problem of lacking feedback data.
@@
 
-\textbf{Probabilistic topic models.}  Topic models\cite{blei:lda}\cite{mic:atm}\cite{mark:prob} are proposed for automated extraction of useful semantic information from corpus data, which are widely used in information retrieval, document annotation, etc.
-The main step is extracting latent factors from corpus, named topics, which are commonly probabilistic distribution over words.
+\textbf{Probabilistic Topic Models.}  Topic models\cite{blei:lda}\cite{mic:atm}\cite{mark:prob} are proposed for automated extraction of useful semantic information from corpus data, which are widely used in information retrieval, document annotation, etc.
+The main step is extracting latent factors from the corpus, named topics, which are commonly probabilistic distributions over words.
 Topic models have three major advantages over other document modeling methods.
@@
 Secondly, latent topics are interpretable respectively, so that extracted results are understandable for users.
-Finally, each document may consist of multiple topics, document can be considered as probabilistic distribution over topics.
-Many existing models regard documents as mixtures of topics, such as pLSI, LDA.
-The author topic model is a generative model that extends LDA to include authorship information for document modeling.
-In our approach, topic model is innovatively applied to identify users.
+Finally, each document may consist of multiple topics and it can be considered as probabilistic distributions over topics.
+Many existing models regard documents as mixtures of topics, such as pLSI and LDA.
+The author-topic model is a generative model that extends LDA to include authorship information for document modeling.
+In our approach, the topic model is innovatively applied to identify users.
 \par
 
-\textbf{Shared account recommendation.} Some work aims at addressing the challenge of identifying current users who share a single account.
-A top-N recommendation for shared accounts approach was proposed by Koen et al.\cite{koen:top-n} It is an item-based top-N collaborative filtering recommender system on binary, positive-only feedback.
-Another method proposed by Santosh et al.\cite{kabbur:nlmf} models users within an account with a much richer representation.
+\textbf{Shared Account Recommendation.} Some work aims at addressing the challenge of identifying users who share a single account.
+A top-$N$ recommendation for shared account  was proposed by Koen et al\cite{koen:top-n}.
+It is an item-based top-$N$ collaborative filtering recommender system on binary and positive-only feedbacks.
+Another method proposed by Santosh et al.\cite{kabbur:nlmf} models users in an account with a much richer representation.
 It uses a nonlinear matrix factorization methods for predicting the recommendation score.
@@
 \label{sec:mod}
-In this Section, we propose a generic model for predicting the probabilistic distribution of passengers under certain contextual environment.
-Finally we integrate user prediction into recommendation to get higher accuracy.
+In this Section, we propose a generic model for predicting the probabilistic distribution of passengers, which can be used for recommendation.
 Figure 2 shows an overview of the recommendation process.
-At first,a dataset for orders are stored, each account may contains several passengers.
-We use this data to train user prediction model as well as extract preference at user granularity.
-Before a recommendation process starts, we calculate user distribution probability applying trained model and contextual knowledge of current session.
-At the final step, we generate a ranked candidate list as the recommendation result based on user prediction result and user's preference.\par
+At first, a dataset of orders is saved into the database, in which each account may correspond to several passengers.
+We use this dataset to train the passenger prediction model as well as to extract passengers' preferences.
+Before a recommendation process starts, we calculate passenger distribution probability applying trained model and contextual information of current session.
+At the final step, we generate a ranked candidate list as the recommendation result based on passenger prediction and passengers' preference information.\par
 \begin{figure}[!hbt]
@@
 Topic models are widely used in recommender systems.
-For example, in pLSA model\cite{tomas:coll}, a topic is a multinomial distribution over items, it represents the latent feature.
-And an account is a multinomial distribution over topics, it can represent the preference of an account.
-Each purchase can be regarded a sample that selects a topic z from account a, and takes an item from topic z.\par
-When topic model is applied to flight recommendation, there are some challenges.
-Firstly, the concepts behind flight tickets are quite different to be modeled.
-Conventional items only have static features, means that the content of an item is less likely to change in the future.
+For example, in pLSA model\cite{tomas:coll}, a topic is a multinomial distribution over items and it represents a latent feature.
+An account is a multinomial distribution over topics and it can represent the preferences of an account.
+Each purchase can be regarded a sample that selects a topic $z$ from account $a$, and takes an item from topic $z$.\par
+When the topic model is applied to flight recommendation, there are some challenges.
+Firstly, the concepts behind flight tickets are quite difficult to be modeled.
+Conventional items only have static features, which means that the contents of an item are less likely to change in the future.
 For flight tickets, however, the price changes frequently even for the same flight number and class.
-Since the price factor plays a significant role in users' choice, so we can't consider the ticket of different price as one item.
+Since the price factor plays a significant role in users' choice, so we can't consider the tickets with different prices as different items.
 Secondly, the amount of tickets for a flight is limited, which leads to a very sparse user-item matrix so that we can't use a collaborative-filtering like method directly.\par
@@
 Some factors are discrete while others are continuous.
-For continuous factors, we can partition them into discrete non-overlapping intervals applying .
-Thus, the number of discrete alternatives of each factor is also very limited.
+For continuous factors, we can partition them into discrete non-overlapping intervals.
+Thus, the number of discrete alternative values of each factor is also very limited.
 We take orders within each account as a corpus.
@@
 \begin{tabular}{|c|c|} \hline
-$M$ & number of accounts within dataset\\ \hline
+$M$ & number of accounts within the dataset\\ \hline
 $V$ & number of words in vocabulary\\ \hline
@@
 $P_i$ & passengers for order $O_i$ \\ \hline
-$F$ & selected Factors\\ \hline
+$F$ & selected factors\\ \hline
 $V$ & size of vocabulary\\ \hline
@@
 
-In author-topic model\cite{deiv:corpora}, a predefined vocabulary is generated containing discrete alternatives and intervals of all selected factors, we use integers to donate each entry in vocabulary.
-The model discovers both topics distributed in an order and passengers associated with distribution of topics.
-We treat every order as a bag of words, thus deduces each order to a vector of word counts.
+In author-topic model\cite{deiv:corpora}, a predefined vocabulary is generated containing discrete alternatives and intervals of all selected factors, we use integers to donate each entry in the vocabulary.
+The model discovers both topics distributed in an order and passengers associated with the distribution of topics.
+We treat every order as a bag of words, thus deduce each order to a vector of word counts.
 An order can be considered as a document with fixed word length, which can be represented as a vector of integers.
@@
 
-For an account M, we generate the observed passenger list $P$.
+For an account $M$, we generate the observed passenger list $P$.
 We denote authors' distribution over topics by a $|P| \times K$ matrix $\Theta$.
@@
 
-To generate a word, we need draw two latent variables, respectively a passenger and a topic.
-First we draw a passenger uniformly from $P$, then a topic $Z$ from $\Theta_A$ and a word w from $\Phi_Z$.
-The following process describes generative model mathematically.\par
+To generate a word, we need draw two latent variables,  a passenger and a topic, respectively.
+First we draw a passenger uniformly from $P$,  a topic $Z$ from $\Theta_A$ and a word $w$ from $\Phi_Z$.
+The following process describes the generative model mathematically.\par
 
@@
 \includegraphics[scale=.55]{f1.eps}
-\caption{Probability Graph for the author-topic model}
+\caption{Probability Graph for the Author-Topic Model}
 \label{fig:mod}
@@
 Figure \ref{fig:mod} shows the graphical model corresponding to this process, where shaded and non-shaded nodes represent observed and unobserved variables respectively.
-It's a plate notation, the number at the bottom of each box indicates repeated times of operation.
+It's a plate notation, the number at the bottom of each box indicates repeated times of the operation.
 Arrows represents the conditional dependency between variables.
@@
 
-\subsection{Parameter inference}
-As mentioned above, the author-topic model includes two sets of unknown parameters, the $P$ passenger-topic distributions $\theta$, and the $K$ topic-word distributions $\phi$.
+\subsection{Parameter Inference}
+As mentioned above, the author-topic model includes two sets of unknown parameters, the $P$ passenger-topic distributions $\theta$ and the $K$ topic-word distributions $\phi$.
 There are a variety of algorithms that can be applied to estimate the parameters of author-topic models, the Expectation-Maximization algorithm and Gibbs sampling\cite{gregor:esti}.
-Generic EM algorithms are likely to face local maxima and computational inefficient.
-In this paper, we utilize Gibbs sampling, it does not explicitly estimate parameters, instead, it evaluates posteriori distribution just on drawn passenger $X$ and topic $Z$.
+Generic EM algorithms are likely to face local maximum and computational inefficiency problems.
+Here we utilize Gibbs sampling because it does not explicitly estimate parameters, instead, it evaluates posteriori distribution just based on drawn passengers $X$ and topics $Z$.
 Thus it is simple for Dirichlet priors.\par
@@
 With the above generative model, $P(x_{oi}=p|\mathbf{p}_o)$ is assumed to be a uniform distribution over passenger list $P$.
-Each topic is drawn independently when conditioned on $\Theta$ and $p_o$, and each word is drawn independently when conditioned on $\Phi$ and $z$.
+Each topic is drawn independently conditioned on $\Theta$ and $p_o$, and each word is drawn independently  conditioned on $\Phi$ and $z$.
 Equation \ref{eq:1} can be applied as the likelihood of all orders in a single account.
@@
 In general, every word in the corpus should be sampled, and the batch sampling process will be performed for several iterations.
-Gregor\cite{gregor:esti} constructs a Markov chain that converges to the posteriori distribution on passenger $x$ and topic $z$.
-$p(\Theta,\Phi|\mathbf{z},\mathbf{x},\alpha,\beta)$ can be calculated by the property that Dirichlet distribution is conjugate to the multinomial distribution.
-Each pair of passenger and topic $(z_i,x_i)$ is drawn with the following equation:\\
+A Markov chain \cite{gregor:esti} can be constructed that converges to the posteriori distribution on passenger $x$ and topic $z$.
+$p(\Theta,\Phi|\mathbf{z},\mathbf{x},\alpha,\beta)$ can be calculated in terms of the property that Dirichlet distribution is conjugate to the multinomial distribution.
+Each pair of passenger and topic $(z_i,x_i)$ is drawn according to the following equation:\\
 \begin{flalign}
@@
 \end{flalign}\\
-Equation \ref{eq:2} represents the probability of assigning topic t and passenger p for i-th word in order o.
-$C^{WT}$ is the word-topic matrix, and $C_{wt}$ is the number of times word $w$ is assigned to topic $t$ except for the current word.
-$C^{TP}$ represents the topic-passenger matrix, and $C_{tp}$ indicates the number of times passenger $p$ is assigned to topic $t$ except for the current word $w_{oi}$.
-$W$ is the size of vocabulary, $T$ represents the number of topics and $P$ is the number of passengers.
+Equation \ref{eq:2} represents the probability of assigning topic $t$ and passenger $p$ for $i$-th word in order $o$.
+$C^{WT}$ is the word-topic matrix, and $C_{wt}$ is the times that word $w$ is assigned to topic $t$ except for the current word.
+$C^{TP}$ represents the topic-passenger matrix, and $C_{tp}$ indicates the times that passenger $p$ is assigned to topic $t$ except for the current word $w_{oi}$.
+Moreover, $W$ is the size of vocabulary, $T$ represents the number of topics and $P$ is the number of passengers.
 From the sampling metric, we can estimate the topic-word distribution and passenger-topic distribution:\\
@@
 where $\theta_{tp}$ is the probability of drawing topic $t$ conditioned on passenger $p$ and $\phi_{wt}$ is the probability of drawing word $w$ conditioned on topic $t$.
-Thus in the process of parameter inference, we need to keep matrix $C^{TP}$ and $C^{WT}$, besides, the sampled word-topic list $T$ and sampled word-passenger list $P$ should be updated after each sample, where $T[o][i]$ represents the topic sampled for word i in order o, and $P[o][i]$ represents the passenger sampled.\par
-The algorithm performs in three steps, respectively, initialization, sampling and updating.
-At the first step, we assign each word in corpus with random passengers and topics.
+Thus in the process of parameter inference, we need to keep matrix $C^{TP}$ and $C^{WT}$, besides, the sampled word-topic list $T$ and sampled word-passenger list $P$ should be updated after each sampling, where $T[o][i]$ represents the topic sampled for word $i$ in order $o$ and $P[o][i]$ represents the passenger sampled.\par
+The algorithm performs in three steps, i.e., initialization, sampling and updating respectively.
+At the first step, we assign each word in the corpus with random passengers and topics.
 Then for every topic $t$, we count the frequency of each vocabulary item assigned with $t$.
 For every passenger $p$, we count the frequency of each $K$ topic assigned with $p$.
-For every sampling operation, a word in corpus is chosen, the probability of topic distribution and passenger distribution is calculated conditioned on the rest words in corpus applying Equation \ref{eq:2}, with these two probability, we can sample a new topic and passenger for the current word.
-After several batch iterations, the passenger-topic matrix $\Theta$ and topic-word matrix $\Phi$ can be updated applying Equation \ref{eq:3}, \ref{eq:4}.
-So the computational efficiency is the number of words multiplies number of topics, passengers, and iteration times.\par
+For every sampling operation, a word in corpus is chosen, the probability of topic distribution and passenger distribution is calculated conditioned on the rest words in corpus by applying Equation \ref{eq:2}, with these two probabilities, we can sample a new topic and passenger for the current word.
+After several batch iterations, the passenger-topic matrix $\Theta$ and topic-word matrix $\Phi$ can be updated by applying Equation \ref{eq:3}, \ref{eq:4}.
+So the computational efficiency is the number of words multiplies number of topics, passengers and iteration times.\par
 \subsection{Passenger Prediction}
 Given the passenger topic probability matrix $\Theta$ and topic-word probability matrix $\Phi$.
-We can predict passengers for an anonymous order and a set of passengers.
+We can predict passengers for an anonymous order.
 It's essentially a classification of an unlabeled order\cite{shanshan:unpopular}.
-We perform the classification by choosing the passengers who maximizes the probability $p(p|o_n)$, represented in the following equation:\\
+We perform the classification by choosing the passenger whose apperance can maximize the probability $p(p|o_n)$, represented in the following equation:\\
 \begin{equation}
@@
 \end{equation}\\
-where $p(p) = |O_p| / |O|$, $|O_p|$ is the number of orders participated by passenger p.
-$p(w|t,p) = p(t|p) \times p(w|t)$ since the process of drawing topic form a passenger and drawing word from a topic are independent from each other.
-$p(t|w)$ represents the probability that word w is assigned to topic t, which can be computed by $\frac{C^{wt}}{\sum_w'C^{w't}}$.\par
-One important issue is how to determine the number of passengers.
-Through statistic analysis we find that most of test orders have exactly one passenger.
-In average, the probability of every passenger is $P_A = \frac{1}{|P|}$.
-We decide the passenger number by omitting passengers whose probability is not greater than $P_A$.
-We show the evaluation metric and prediction result in section 4.3.\par
+where $p(p) = |O_p| / |O|$, $|O_p|$ is the number of orders participated by passenger $p$.
+$p(w|t,p) = p(t|p) \times p(w|t)$ since the process of drawing topic from a passenger and drawing a word from a topic are independent of each other.
+$p(t|w)$ represents the probability that word $w$ is assigned to topic $t$, which can be computed by: $\frac{C^{wt}}{\sum_w'C^{w't}}$.\par
+One important issue here is how to determine the number of passengers.
+Through statistic analysis we find that most of testing orders have exactly one passenger.
+On average, the probability of every passenger is $P_A = \frac{1}{|P|}$.
+We determine the passenger number by omitting passengers whose probability is not greater than $P_A$.
+We show the evaluation metric and prediction result in Section 4.3.\par
 In conclusion, the passenger prediction task can be partitioned into two steps.
-For the first step, a set of decisive factors are extracted by domain field knowledge to generate a vocabulary.
+For the first step, a set of decisive factors are extracted based on domain  knowledge to generate a vocabulary.
 And the parameter $\Theta$ and $\Phi$ are trained through several batches of Gibbs sampling.
-In the second step, passengers of an anonymous order can be predicted applying Equation \ref{eq:5}.
+In the second step, passengers of an anonymous order can be predicted by applying Equation \ref{eq:5}.
 Algorithm \ref{alg:1} describes the predicting process mathematically.\par
@@
 \label{sec:rec}
-Since there is little existing work aimed at flight ticket recommendation.
+There is little existing work aiming at providing flight recommendation.
 In this section, we propose a user preference-based recommendation approach.
-In section \ref{sec:exp}, we will evaluate this method as well as some business ranking strategies, such as price rank etc, to demonstrate that this method has a better accuracy.
-Then, we will apply the passenger prediction results to improve recommendation accuracy further on.
+In Section \ref{sec:exp}, we evaluate this method against some ranking strategies, such as price rank etc, to demonstrate that this method has a better accuracy.
+Then, we will apply the passenger prediction results to improve recommendation accuracy further.
 
 \subsection{Factor selection and frequency statistic}
-A flight ticket clearly contains a set of factors, such as price, takeoff time, craft size, etc.
-Thus some decisive factors should be chosen.
-Besides, these factors may be either discrete or continuous.
-We divide a continuous factor into a vector of intervals, so any factor can be represented as a vector of finite alternatives.
+A flight ticket contains a set of attributes such as price, takeoff time, craft size, etc.
+We should select some of them as the decisive factors.
+These attributes may be either discrete or continuous variables.
+We divide a continuous attribute into a vector of intervals, so any factor can be represented as a vector of finite alternatives.
 Then, we analyze user's submitted orders by counting the frequency of all alternatives for each factor.
@@
 \label{sec:exp}
-In the following subsections, we introduce datasets and evaluation metrics. Then we evaluate the performance of user prediction and passenger prediction based recommendation respectively.
+In the following subsections, we introduce datasets and evaluation metrics. Then we evaluate the performance of passenger prediction and passenger prediction based recommendation respectively.
 \subsection{Dataset}
@@
 Besides, an order contains some travel information that can be considered as decisive factors, such as departure airport, arrival airport, takeoff time, etc.
-In our experiment, we select active users whose amount of history orders reaches a threshold, thus user's preference can be extracted with more confidence.
+In our experiment, we select active users whose amount of historical orders reaches a threshold, thus passengers' preferences can be extracted with more confidence.
 In addition, many researches\cite{amy:guess}\cite{yutaka:modeling} on shared account recommendation generate an artificial dataset by composing single accounts' data.
-We also generate an artificial dataset combining single passengers from different accounts.
-We extract two passengers from arbitrary accounts and combine them as one account.
-Overviews of two datasets and the meta data of orders are summarized in table \ref{tab:dat} and table \ref{tab:mdat}.
+We also generate an artificial dataset combining single passengers' data from different accounts.
+The overviews of these two datasets and the meta data of orders are summarized in table \ref{tab:dat} and table \ref{tab:mdat}.
 \begin{table}[!htbp]
@@
 \subsection{Settings and Evaluation Metrics}
-Essentially, flight ticket recommendation is an approach to select the best matched ticket by measuring the similarities between candidate tickets and user's preferences.
+Essentially, flight  recommendation is a process to select the best matched ticket by measuring the similarities between candidate tickets and user's preferences.
 We take the latest order of a user as the test data and the rest ones as the training data.
-The test data also plays a role of providing contextual knowledge for user prediction.\par
-One significant issue is that we can't know real candidates at the time when user performed the search action.
-Fortunately, we can get an approximate set of candidate by collecting orders from all users in dataset with the same order date, takeoff date, departure city and arrival city as the test order, the granularity of the simulate candidate is to every flight, class and price range.
-Price range is a discrete interval representing the degree of the price based on domain knowledge.
-In order to get a persuasive evaluation result, we filter out test orders with the size of candidate list less than 20, and the average size of candidates is 45.\par
+The test data also plays a role of providing contextual information for user prediction.\par
+One significant issue is that we can't know real candidates at the time when a user performs the search action.
+Fortunately, we can get an approximate set of candidates by collecting orders from all users in the dataset with the same order date, takeoff date, departure city and arrival city as the test order, the granularity of the simulate candidate is to every flight, class and price range.
+Price level is a discrete interval representing the scale of the price based on domain knowledge.
+In order to get a convincing evaluation result, we filter out test orders with the size of candidate list less than 20 and the average size of candidates is 45.\par
 We apply two commonly used metrics MAP(Mean Average Precision) and top-$N$ hit rate to evaluate the recommendation performance. The definition of MAP is described as follow:\\
@@
 The results demonstrate that our model has a higher prediction precision than the random method on both datasets.
-We notice that the average improvements of prediction accuracy on artificial dataset is higher than on the real dataset.
+We notice that the average improvements of prediction accuracy on artificial dataset are higher than on the real dataset.
 Besides, when the topic number is 10 or 15, both datasets get the best performance while the performance goes down with the topic number increasing.
@@
 \subsection{Recommendation}
-After obtaining the predicted probabilistic distribution of passengers, we can extend preference based recommendation approach by only extracting preferences of predicted passengers.
+After obtaining the predicted probabilistic distribution of passengers, we can extend preference based recommendation approach by  extracting preferences of predicted passengers.
 If there are multiple predicted passengers for one test order, we generate a composite preference model that combines all involved passenger's preferences together.
-The probability of every passenger is normalized.\par
+\par
 We use MAP and top-$N$ hit rate mentioned above to evaluate recommendation performance.
@@
 The transfered preference based method is the same as the previous one except it takes the difference between flight distribution of various air routes into consideration.
-This method groups training data by route, and evaluates similarity between routes by flight distribution in some attributes such as airline, class, price range.
-If a user isn't active in target route, we transfer his preferences from most similar active routes with a transfer rate.
+This method groups training data by route, and evaluates similarity between routes by flight distribution on some attributes such as airline, class and price level.
+If a passenger isn't active on the target route, we transfer his preferences from most similar active routes with a transfer rate.
 In our experiment, the transfer rate is  $ \alpha = 0.5$.
-Price rank is a simple strategy that ranks candidates by price in an ascending order.
-Hot rank is a strategy that ranks candidates according to the hotness, which is based on the total order amount within a period of the previous two weeks, items are distinguished by flight number, class and price range.\par
+Price rank is a simple strategy that ranks candidates based on price in an ascending order.
+Hot rank is a strategy that ranks candidates according to the popularities, which is based on the total order amount within a period of the previous two weeks.
+\par
 
@@
 \end{figure}\par
-Figure \ref{fig:top} and \ref{fig:rank} show recommendation accuracy for real dataset and artificial dataset respectively.
+Figure \ref{fig:top} and \ref{fig:rank} show recommendation accuracy on the real dataset and artificial dataset respectively.
 The figure's horizontal axis shows the number of top-$N$ recommended flights.
@@
 The result shows that the baseline recommendation approach performs much better than price rank strategy.
-And content based recommendation combined with passenger prediction can achieve higher accuracy than baseline method.
-We have noticed the improvement in artificial dataset is larger than real dataset.
-The reason may be that passengers in artificial dataset have more difference preferences from each other.
-In addition, passengers in the same account may book tickets for others at real data set, thus reducing the variety of passengers preference.
+And content based recommendation combined with passenger prediction can achieve a higher accuracy than baseline method.
+We can also notice that the improvements on the artificial dataset is larger than on the real dataset.
+The reason may be that passengers in artificial dataset have more diversified preferences since they are randomly selected and composed.
 
@@
 \label{sec:con}
-In this paper, we proposed a generic probabilistic model to predict passengers in a single flight ticket booking account based on passengers' historical submitted orders.
-This model is also appropriate for scenarios that individuals can be explicitly identified, such as online hotel booking.
+In this paper, we proposed a generic probabilistic model to predict passengers in a single flight booking account based on passengers' historical submitted orders.
+This model is appropriate for scenarios that individuals can not be explicitly identified before placing the order, such as online hotel booking.
 For specified contextual environment, we can make a prediction for passenger distribution.
-Then we integrate user prediction into recommendation process.
+Then we integrate passenger prediction into recommendation process.
 For experiment evaluation, we propose a general preference based recommendation approach for implicit feedback, and verify the efficiency of proposed model on two datasets.

### 2016-07-10 Paper.tex
Add files via upload

@@
 Recent years, with the rapid development of online travel agencies, there are more and more passengers booking flights through online travel service providers.
-Typically, an user may input his departure city , arrival city  and departure time, then he will get a list of candidate flights.
-In general, there are dozens of flights within a list .
-Figure \ref{fig:res} shows a list for all candidate flights  from Beijing to Hong Kong when input a query.
-There are total 156 matchable flights and the website only provides simple sorting strategies such as departure time, arrival time or price.
+Typically, an user may input his departure city, arrival city and departure time, then he will get a list of candidate flights.
+In general, there are dozens of flights within a list.
+We perform a search for flights from Beijing to Hong Kong at a website, there are total 156 matchable flights.
+The website only provides simple sorting strategies such as departure time, arrival time or price.
 Thus, it may take quite a long time for users to find the appropriate one.
 Therefore, a recommender system is necessary for better user experiences.
-\begin{figure}[!hbt]
-\centering
-\includegraphics[scale=.48]{flight_tickets.eps}
-\caption{Search result for flight tickets}
-\label{fig:res}
-\end{figure}\par
-Essentially, a recommender system is used for generating a personalized ranking on a set of items\cite{lv:rec}.
+
+\par Essentially, a recommender system is used for generating a personalized ranking on a set of items\cite{lv:rec}.
 Typical recommender systems assume that the preference model of an individual can be learned from each account.
@@
 Moreover, so far, the experiments have only been evaluated on artificial composite datasets.
+\par
 The flight booking service providers can acquire passenger's personal information after he has submitted the order.
@@
 To achieve this target, we adopt the probabilistic author-topic model to analyze passengers' behaviors.
-We regard all historical orders in an account as the corpus, all passengers appearing in the account as authors and orders together with context information as documents.
-Note that if an order has more than one passenger, they are regarded as co-authors of this document.\par
+We regard all historical orders in an account as the corpus, all passengers appearing in the account as authors and orders together with context information as documents.\par
 In experiment section, we apply our method to a real flight order dataset. And the result shows that our method has higher identification accuracy and a better recommendation accuracy.\par
@@
 Content-based recommender systems \cite{tech:cset}\cite{lops:handbook}are appropriate for highly structured items.
-The method needs proper representations of the attributes of items and the profile of user interests, then it tries to match  the profile of user's interests with attributes of items.
-In general, a content-based recommender system consists of three components.
-A content analyzer extracts structured attributes of items through a series of pre-processing steps and it produces the inputs for the system, which always needs domain related knowledge.
-A profile learner analyzes and constructs users' profiles of interests by collecting users' historical behaviors.
-In addition, this component also relies on feedbacks of users.
-A filtering component evaluates the relevances of items to particular users by matching them with users' profiles and the outputs can be either binary or continuous.
-In this stage, some similarity measurements including cosine or euclidean distance can usually be applied.\par
+The method needs proper representations of the attributes of items and the profile of user interests, then it tries to match the profile of user's interests with attributes of items.\par
 \textbf{Flight Ticket Recommendation.} There is little work focusing on personalized flight  recommendations.
-Many online flight booking agencies provide sorting and filtering strategies to improve users' experiences, such as sorting by price or takeoff time and filtering by airline or departure city.
-Others also provide additional information that can help users, for example, placing the most popular flights at the top or highlighting some of them.
+Many online flight booking agencies provide sorting and filtering strategies to improve users' experiences, such as sorting by price and filtering by airline etc.
 These methods do make sense in helping users find appropriate flights within less time.
 However, they can not provide personalized recommendations.
+Flight recommendation mainly bases on implicit feedback\cite{song:mining}, which suffers from problems of data noises and lack of negative feedbacks.
 In 2004, Lorcan Coyle\cite{lor:flight} proposed a Personal Travel Assistant(PTA).
-PTA is based on case-based reasoning, which takes users' historical orders as cases and recommends the most similar candidate flights to users' queries.
-In addition, PTA also proposes the attribute weight training and case storage method.\par
-\textbf{Implicit Feedback.} The users' feedbacks can be divided into implicit or explicit type.
-The explicit feedbacks can be acquired from users' ratings or text comments.
-However,  users may not willing to provide explicit feedbacks since it needs additional efforts.
-Moreover, in many applications, a single numeric rating may not be adequate for describing users feeling to an item.
-Implicit feedback methods\cite{song:mining} try to infer users' attitudes to an item based on their behaviors, such as clicking, collecting or bookmarking et al.
-It has the advantage of being free from the problem of lacking feedback data.
-Nevertheless, implicit feedback based recommender suffers from problems of lack of negative feedbacks and data noises.
-In order to provide recommendations when only implicit feedbacks are available, some methods are proposed, such as one class collaborative filtering and content based recommender.\par
+PTA is based on case-based reasoning, which takes users' historical orders as cases and recommends the most similar candidate flights to users' queries.\par
 
-\textbf{Probabilistic Topic Models.}  Topic models\cite{blei:lda}\cite{mic:atm}\cite{mark:prob} are proposed for automated extraction of useful semantic information from corpus data, which are widely used in information retrieval, document annotation, etc.
+\textbf{Probabilistic Topic Models.}  Topic models\cite{blei:lda}\cite{mic:atm}\cite{mark:prob} are proposed for automated extraction of useful semantic information from corpus data.
 The main step is extracting latent factors from the corpus, named topics, which are commonly probabilistic distributions over words.
-Topic models have three major advantages over other document modeling methods.
-At first, topic models provide a completely unsupervised approach to extract topics, thus requiring no document labels and no initialization.
-Unsupervised methods are necessary for modeling large document corpus, besides, in some fields, with the rapid change of content's topics, predefined topic categories may not reflect the development of specific field.
-Secondly, latent topics are interpretable respectively, so that extracted results are understandable for users.
-Finally, each document may consist of multiple topics and it can be considered as probabilistic distributions over topics.
-Many existing models regard documents as mixtures of topics, such as pLSI and LDA.
+Topic models provide a completely unsupervised approach to extract topics, thus requiring no document labels and no initialization.
+Besides, each document may consist of multiple topics and it can be considered as probabilistic distributions over topics.
 The author-topic model is a generative model that extends LDA to include authorship information for document modeling.
@@
 In this Section, we propose a generic model for predicting the probabilistic distribution of passengers, which can be used for recommendation.
-Figure 2 shows an overview of the recommendation process.
+Figure \ref{fig:over} shows an overview of the recommendation process.
 At first, a dataset of orders is saved into the database, in which each account may correspond to several passengers.
@@
 Since the price factor plays a significant role in users' choice, so we can't consider the tickets with different prices as different items.
-Secondly, the amount of tickets for a flight is limited, which leads to a very sparse user-item matrix so that we can't use a collaborative-filtering like method directly.\par
+Secondly, the amount of tickets for a flight is limited, which leads to a very sparse user-item matrix so that we can't use a collaborative-filtering like method directly.
 Fortunately, the decisive factors of a flight ticket are quite fixed, such as airline, takeoff time, price and class etc.
-Some factors are discrete while others are continuous.
-For continuous factors, we can partition them into discrete non-overlapping intervals.
-Thus, the number of discrete alternative values of each factor is also very limited.
-We take orders within each account as a corpus.
+The number of alternatives for each factor is also quite limited.\par
 Our notations are summarized in table \ref{tab:not}.\par
@@
 
-In author-topic model\cite{deiv:corpora}, a predefined vocabulary is generated containing discrete alternatives and intervals of all selected factors, we use integers to donate each entry in the vocabulary.
-The model discovers both topics distributed in an order and passengers associated with the distribution of topics.
+In author-topic model\cite{deiv:corpora}, a predefined vocabulary is generated containing discrete alternatives and intervals of all selected factors.
 We treat every order as a bag of words, thus deduce each order to a vector of word counts.
-An order can be considered as a document with fixed word length, which can be represented as a vector of integers.
-All passengers corresponding to an order are co-authors for that document.
-Each passenger is associated with a multinomial distribution over topics and each topic is associated with a multinomial distribution over entries.
-The model essentially reduces dimensions of documents, depending on the amount of topics.\par
+Each passenger is associated with a multinomial distribution over topics and each topic is associated with a multinomial distribution over entries.\par
 
 For an account $M$, we generate the observed passenger list $P$.
-We denote authors' distribution over topics by a $|P| \times K$ matrix $\Theta$.
+We denote passengers' distribution over topics by a $|P| \times K$ matrix $\Theta$.
 The multinomial distribution can be generated from Dirichlet prior distribution with hyper-parameter $\alpha$.
@@
 \end{enumerate}
-\begin{figure}[!hbt]
-\centering
-\includegraphics[scale=.55]{f1.eps}
-\caption{Probability Graph for the Author-Topic Model}
-\label{fig:mod}
-\end{figure}\par
-Figure \ref{fig:mod} shows the graphical model corresponding to this process, where shaded and non-shaded nodes represent observed and unobserved variables respectively.
-It's a plate notation, the number at the bottom of each box indicates repeated times of the operation.
-Arrows represents the conditional dependency between variables.
-In the author-topic model, observed variables include words in an order and the passengers of the order.
 
@@
 As mentioned above, the author-topic model includes two sets of unknown parameters, the $P$ passenger-topic distributions $\theta$ and the $K$ topic-word distributions $\phi$.
-There are a variety of algorithms that can be applied to estimate the parameters of author-topic models, the Expectation-Maximization algorithm and Gibbs sampling\cite{gregor:esti}.
 Generic EM algorithms are likely to face local maximum and computational inefficiency problems.
-Here we utilize Gibbs sampling because it does not explicitly estimate parameters, instead, it evaluates posteriori distribution just based on drawn passengers $X$ and topics $Z$.
+Here we utilize Gibbs sampling\cite{gregor:esti} because it does not explicitly estimate parameters, instead, it evaluates posteriori distribution just based on drawn passengers $X$ and topics $Z$.
 Thus it is simple for Dirichlet priors.\par
@@
 At the first step, we assign each word in the corpus with random passengers and topics.
-Then for every topic $t$, we count the frequency of each vocabulary item assigned with $t$.
-For every passenger $p$, we count the frequency of each $K$ topic assigned with $p$.
 For every sampling operation, a word in corpus is chosen, the probability of topic distribution and passenger distribution is calculated conditioned on the rest words in corpus by applying Equation \ref{eq:2}, with these two probabilities, we can sample a new topic and passenger for the current word.
@@
 $p(t|w)$ represents the probability that word $w$ is assigned to topic $t$, which can be computed by: $\frac{C^{wt}}{\sum_w'C^{w't}}$.\par
-One important issue here is how to determine the number of passengers.
-Through statistic analysis we find that most of testing orders have exactly one passenger.
-On average, the probability of every passenger is $P_A = \frac{1}{|P|}$.
-We determine the passenger number by omitting passengers whose probability is not greater than $P_A$.
-We show the evaluation metric and prediction result in Section 4.3.\par
 In conclusion, the passenger prediction task can be partitioned into two steps.
@@
 
-\begin{algorithm}[htb]
-\caption{trainATM}
-\begin{algorithmic}[1]
-\label{alg:2}
-\REQUIRE
-Word vector $\overrightarrow{W}$. \par
-A test anonymous order $to$
-\ENSURE 
-User-topic parameter $\Theta$ \par
-Topic-word parameter $\Phi$
-\STATE $nak , nkv, nak\_sum, nkv\_sum \leftarrow \mathbf{0}$
-\FORALL{List o : $\overrightarrow{W}$}
-\FORALL{Word w : o}
-\STATE pick a topic $t$ and a user $p$ Multinomial;
-\STATE user-topic count $nak[p][t] += 1$;
-\STATE user-topic sum $nak\_sum[p] += 1$;
-\STATE topic-word count $nkv[t][w] += 1$;
-\STATE topic-word sum $nkv\_sum[t] += 1$;
-\ENDFOR
-\ENDFOR
-\WHILE {not reach iteration limit}
-\FORALL{List o : $\overrightarrow{W}$}
-\FORALL{Word w : o}
-\STATE $nak[p][t] -= 1, nak\_sum[p] -= 1$;
-\STATE $nkv[t][w] -= 1, nkv\_sum[t] -= 1$;
-\STATE sample a new user $p'$ and topic $t'$ by Equation \ref{eq:2};
-\STATE $nak[p'][t'] += 1, nak\_sum[p'] += 1$;
-\STATE $nkv[t'][w] += 1, nkv\_sum[t'] += 1$;
-\ENDFOR
-\ENDFOR
-\ENDWHILE
-\STATE calculate $\Theta,\Phi$ by Equation \ref{eq:3} ,\ref{eq:4};
-\RETURN $\Theta,\Phi$;
-\end{algorithmic} 
-\end{algorithm}
-
 \section{The Preference-based recommendation approach}
@@
 \subsection{Factor selection and frequency statistic}
-A flight ticket contains a set of attributes such as price, takeoff time, craft size, etc.
-We should select some of them as the decisive factors.
+A flight ticket contains a set of attributes.
 These attributes may be either discrete or continuous variables.
-We divide a continuous attribute into a vector of intervals, so any factor can be represented as a vector of finite alternatives.
-Then, we analyze user's submitted orders by counting the frequency of all alternatives for each factor.
-In a word, a user's preference model can be described as a union of vectors, a vector indicates one factor and an element within one vector represents the frequency of corresponding alternative which the user has chosen.\par
+We divide continuous attribute into a list of intervals, for example, takeoff time can be divided into morning, noon, afternoon, night etc.
+Thus, any factor can be represented by finite alternatives.
+Then, we count the distribution of alternatives from a user's historical orders to analyze user's preference on corresponding factor.
+In a word, the preference model can be described as a union of vectors, a vector indicates one factor and an element within one vector represents the frequency of corresponding alternative which the user has chosen.\par
 We can also represent a candidate flight ticket as a vector, where each element is the corresponding alternative of each factor.
@@
 Since users may care different factors, we introduce personalized weight vector for each user.
-The evaluation of this weight vector contains two steps, initializing and training.
-At the initializing step, we estimate how much a user focuses on a factor through the information entropy, as mentioned in \cite{yang:pers}.
+We estimate how much a user focuses on a factor through the information entropy, as mentioned in \cite{yang:pers}.
 We believe that if a user focuses on a factor, his behavior will be more concentrated.
@@
 \end{equation}\par
-The value $b$ is the base of logarithm, and is usually 2.
-The entropy of every factor can be calculated and initialized as the weight value after normalization.
-Considering that different factors have a variety quantity of alternatives and the user may concern different factors some time later, we update the weight vector once the user submits an order.
-For each submission, we have already produced a ranked list for recommendations, if the user doesn't choose an item (i.e, a ticket) from top-$N$ items, we consider this recommendation fails, so that the weight vector need be retrained to make the rank of selected item improved.
-The concept of weight training is mentioned in \cite{lor:flight}.
-By performing weight training for factors, we hope that the result of recommendation getting better in the future.
-The training procedure is quite straightforward.
-At first a learning rate should be set, such as $\alpha = 0.1$ .
-If the selected item has lower similarity for factor $f$ than items ranked before it, the weight value of this factor should be decreased.
-Otherwise, the weight value should be increased.
-To avoid the problem of over-fitting, we define a maximum number of iteration step.
-So the stop criteria is either $1)$ the rank of selected items can't be improved anymore or $2)$ the procedure reaches the iteration time limitation.\\
+The value $b$ is the base of logarithm, and is usually 2. The entropy of every factor can be calculated and initialized as the weight value after normalization. \par
 The preference based recommendation algorithm is described as Algorithm \ref{alg:3}.
@@
 Items in candidate list are ranked based on inner product of $W$ and corresponding value of factor.
-After every recommendation, the list is retrained and stored depending on the item that user actually chosen.
 
@@
 \STATE $P \leftarrow extractUserPref(O,F)$;
-\STATE $W \leftarrow fetchWeightedList(u)$;
-\IF{$W$ is $null$}
 \STATE initialize $W$ by entropy;
-\ENDIF
 \STATE $R \leftarrow \emptyset$;
@@
 \STATE sort $R$ by score;
-\STATE $trainWeightedList(W,R,P)$;
-\STATE $saveWeightedList(u,W)$;
 \RETURN $R$;
-\end{algorithmic} 
-\end{algorithm}
-
-\begin{algorithm}[htb]
-\caption{extractUserPref}
-\begin{algorithmic}[1]
-\label{alg:4}
-\REQUIRE
-User's history order list $O$. \par
-Predefined discrete factor list $F$
-\ENSURE 
-User's preference list $P$
-\STATE List $P \leftarrow \emptyset$;
-\FORALL {List $f : F$} 
-\STATE append  $List(0,|f|)$  to $P$;
-\ENDFOR
-\FORALL{List $order : O$}
-\FOR{$i: 1 \to |order| $}
-\STATE $P[i][order_i] += 1$;
-\ENDFOR	
-\ENDFOR 
-\RETURN $P$;
-\end{algorithmic} 
-\end{algorithm}
-
-\begin{algorithm}[htb]
-\caption{weightedScore}
-\begin{algorithmic}[1]
-\label{alg:5}
-\REQUIRE \par
-Candidate item $c$ \par
-User's preference list $P$ \par
-User's weight vector $W$ 
-\ENSURE Score of candidate $S$
-\STATE $S \leftarrow 0$;
-\FOR{$i: 1 \to |c| $}
-\STATE $S += \frac{P[i][c_i]}{sum(P[i])} \times W[i]$;
-\ENDFOR
-\RETURN $S$;
-\end{algorithmic} 
-\end{algorithm}
-
-\begin{algorithm}[htb]
-\caption{trainWeightedList}
-\begin{algorithmic}[1]
-\label{alg:6}
-\REQUIRE \par
-Ranked list $R$ \par
-User's Preference list $P$ \par
-User's weight list $W$ \par
-User actually chose candidate $c$
-\ENSURE Trained weighted list $W$
-\STATE $R_c \leftarrow rankOf(R,c)$;
-\STATE $\alpha \leftarrow 0.1$;
-\STATE $count \leftarrow 0$;
-\WHILE {$count < limit$}
-\STATE $BeatList \leftarrow List(false,|W|)$;
-\FOR{$i: 1 \to |W|$}
-\FOR{$j: 1 \to R_c $}
-\IF{$P[i][R_{ji}] > P[i][c_{i}] $}
-\STATE $Beatlist[i] \leftarrow true$;
-\STATE break;
-\ENDIF
-\ENDFOR
-\IF{$BeatList[i] = true$}
-\STATE $BeatList[i] \leftarrow false$;
-\STATE $W[i] \leftarrow W[i] / (1+\alpha)$;
-\ENDIF
-\ENDFOR
-\ENDWHILE
-\STATE $normalize(W)$;
-\RETURN $S$;
 \end{algorithmic} 
@@
 We use desensitized passenger id to distinguish individuals from each other.
-Besides, an order contains some travel information that can be considered as decisive factors, such as departure airport, arrival airport, takeoff time, etc.
 In our experiment, we select active users whose amount of historical orders reaches a threshold, thus passengers' preferences can be extracted with more confidence.
 In addition, many researches\cite{amy:guess}\cite{yutaka:modeling} on shared account recommendation generate an artificial dataset by composing single accounts' data.
-We also generate an artificial dataset combining single passengers' data from different accounts.
+We also generate an artificial dataset combining single passengers' data from two different accounts.
 The overviews of these two datasets and the meta data of orders are summarized in table \ref{tab:dat} and table \ref{tab:mdat}.
@@
 
-The meta data of an order includes travel information, context information, individual information and order information.
-Travel information contains the departure and arrival city, takeoff time.
-Context information contains time of browsing, searching and filtering actions.
-Individual information contains account id, personal information.
-Order information consists of price, seat class, flight number, airline company  et al.\par
-
 \subsection{Settings and Evaluation Metrics}
-Essentially, flight  recommendation is a process to select the best matched ticket by measuring the similarities between candidate tickets and user's preferences.
-We take the latest order of a user as the test data and the rest ones as the training data.
-The test data also plays a role of providing contextual information for user prediction.\par
+We take the latest order of a user as the test data and the rest ones as the training data. The test data also plays a role of providing contextual information for user prediction.\par
 One significant issue is that we can't know real candidates at the time when a user performs the search action.
-Fortunately, we can get an approximate set of candidates by collecting orders from all users in the dataset with the same order date, takeoff date, departure city and arrival city as the test order, the granularity of the simulate candidate is to every flight, class and price range.
-Price level is a discrete interval representing the scale of the price based on domain knowledge.
+Fortunately, we can get an approximate set of candidates by collecting orders from all users in the dataset with the same order date, takeoff date, departure city and arrival city as the test order.
 In order to get a convincing evaluation result, we filter out test orders with the size of candidate list less than 20 and the average size of candidates is 45.\par
@@
 \subsection{Passenger Prediction}
+\label{sub:pred}
 We train a probabilistic model for every account where topic number selected varying ${5,10,\dots,50}$.
@@
 The results demonstrate that our model has a higher prediction precision than the random method on both datasets.
-We notice that the average improvements of prediction accuracy on artificial dataset are higher than on the real dataset.
-Besides, when the topic number is 10 or 15, both datasets get the best performance while the performance goes down with the topic number increasing.
-The sizes of corpus' vocabulary and number of words in each order also impact the optimal topic number.
+Besides, when the topic number is 10 or 15, both datasets get the best performance while the performance goes down with the topic number increasing, which demonstrates that the size of corpus' vocabulary and number of words in each order also impact the optimal topic number.
 In the next subsection, we evaluate the recommendation performance with topic number fixed at 10.\par
@@
 Price rank is a simple strategy that ranks candidates based on price in an ascending order.
-Hot rank is a strategy that ranks candidates according to the popularities, which is based on the total order amount within a period of the previous two weeks.
+Hot rank is a strategy that ranks candidates according to the popularities, which is based on total order amount within a period of previous two weeks.
 \par
@@
 \end{figure}\par
-Figure \ref{fig:top} and \ref{fig:rank} show recommendation accuracy on the real dataset and artificial dataset respectively.
+Figure \ref{fig:top} shows recommendation accuracy on the real dataset and artificial dataset respectively.
 The figure's horizontal axis shows the number of top-$N$ recommended flights.
 The accuracy increases linearly with the growth of recommended flights.
-The result shows that the baseline recommendation approach performs much better than price rank strategy.
+Figure \ref{fig:rank} shows MAP on two datasets.
+The results show that the baseline recommendation approach performs much better than price rank strategy.
 And content based recommendation combined with passenger prediction can achieve a higher accuracy than baseline method.
@@
 Collaborative filtering via gaussian probabilistic latent semantic analysis.
-In: Proceedings of the 26th International ACM conference on Research and development in informaion retrieval,259-266(2004)
+In: Proceedings of the 26th International ACM conference on Research and development in information retrieval,259-266(2004)
 

### 2016-07-17 Paper.tex
Add files via upload

@@
 \documentclass{llncs}
-\bibliographystyle{splncs}
+\bibliographystyle{splncs03}
 \usepackage{enumitem}
@@
 
-\author{Yafeng Zhao, Jian Cao}
+\author{Yafeng Zhao, Jian Cao\thanks{Corresponding Author}, Yudong Tan}
 \institute{Department of Computer Science and Engineering,\\
-Shanghai Jiao Tong University, Shanghai 200240, China\\
-\email{zyfgs2012@163.com, cao-jian@sjtu.edu.cn}}
+Shanghai Jiao Tong University, Shanghai 200240, China and\\
+Air Ticketing B.U., Ctrip.com International, Ltd.\\
+\email{zyfgs2012@163.com,cao-jian@sjtu.edu.cn,ydtan@Ctrip.com}}
 
@@
 \textbf{Paper organization.} The rest of paper is structured as follows.
-We introduce related work in Section \ref{sec:relw}.
-In Section \ref{sec:mod}, we define the problem and describe the model.
+We introduce related work in Sect.\ref{sec:relw}.
+In Sect.\ref{sec:mod}, we define the problem and describe the model.
 Besides, we also discuss how to do parameter inference.
-In Section \ref{sec:rec}, we propose a preference-based flight ticket recommendation approach, which also plays a role as a baseline method at evaluation stage.
-In Section \ref{sec:exp}, we introduce the experiment dataset, evaluation metrics, the experimental results of passenger prediction and flight recommendation.
-Finally, we conclude the paper in Section \ref{sec:con}.
+In Sect.\ref{sec:rec}, we propose a preference-based flight ticket recommendation approach, which also plays a role as a baseline method at evaluation stage.
+In Sect.\ref{sec:exp}, we introduce the experiment dataset, evaluation metrics, the experimental results of passenger prediction and flight recommendation.
+Finally, we conclude the paper in Sect.\ref{sec:con}.
 
@@
 For flight tickets, however, the price changes frequently even for the same flight number and class.
-Since the price factor plays a significant role in users' choice, so we can't consider the tickets with different prices as different items.
+Since the price factor plays a significant role in users' choice, we can't consider the tickets with different prices as different items.
 Secondly, the amount of tickets for a flight is limited, which leads to a very sparse user-item matrix so that we can't use a collaborative-filtering like method directly.
@@
 The number of alternatives for each factor is also quite limited.\par
-Our notations are summarized in table \ref{tab:not}.\par
+Our notations are summarized in Table \ref{tab:not}.\par
 \begin{table}[!htbp]
@@
 Each topic is drawn independently conditioned on $\Theta$ and $p_o$, and each word is drawn independently  conditioned on $\Phi$ and $z$.
-Equation \ref{eq:1} can be applied as the likelihood of all orders in a single account.
+Eq.\ref{eq:1} can be applied as the likelihood of all orders in a single account.
 If we treat $\Theta$ and $\Phi$ as random variables, our target is to estimate the Maximum A Posteriori for the generative model.\par
@@
 \end{flalign}\\
-Equation \ref{eq:2} represents the probability of assigning topic $t$ and passenger $p$ for $i$-th word in order $o$.
+Eq.\ref{eq:2} represents the probability of assigning topic $t$ and passenger $p$ for $i$-th word in order $o$.
 $C^{WT}$ is the word-topic matrix, and $C_{wt}$ is the times that word $w$ is assigned to topic $t$ except for the current word.
@@
 At the first step, we assign each word in the corpus with random passengers and topics.
-For every sampling operation, a word in corpus is chosen, the probability of topic distribution and passenger distribution is calculated conditioned on the rest words in corpus by applying Equation \ref{eq:2}, with these two probabilities, we can sample a new topic and passenger for the current word.
-After several batch iterations, the passenger-topic matrix $\Theta$ and topic-word matrix $\Phi$ can be updated by applying Equation \ref{eq:3}, \ref{eq:4}.
+For every sampling operation, a word in corpus is chosen, the probability of topic distribution and passenger distribution is calculated conditioned on the rest words in corpus by applying Eq.\ref{eq:2}, with these two probabilities, we can sample a new topic and passenger for the current word.
+After several batch iterations, the passenger-topic matrix $\Theta$ and topic-word matrix $\Phi$ can be updated by applying Eq.\ref{eq:3}, Eq.\ref{eq:4}.
 So the computational efficiency is the number of words multiplies number of topics, passengers and iteration times.\par
@@
 And the parameter $\Theta$ and $\Phi$ are trained through several batches of Gibbs sampling.
-In the second step, passengers of an anonymous order can be predicted by applying Equation \ref{eq:5}.
+In the second step, passengers of an anonymous order can be predicted by applying Eq.\ref{eq:5}.
 Algorithm \ref{alg:1} describes the predicting process mathematically.\par
@@
 \STATE Model $M \leftarrow trainATM(W)$;
-\STATE calculate user's probability by Equation \ref{eq:5};
+\STATE calculate user's probability by Eq.\ref{eq:5};
 \FORALL{user : P}
@@
 In this section, we propose a user preference-based recommendation approach.
-In Section \ref{sec:exp}, we evaluate this method against some ranking strategies, such as price rank etc, to demonstrate that this method has a better accuracy.
+In Sect.\ref{sec:exp}, we evaluate this method against some ranking strategies, such as price rank etc, to demonstrate that this method has a better accuracy.
 Then, we will apply the passenger prediction results to improve recommendation accuracy further.
@@
 We also generate an artificial dataset combining single passengers' data from two different accounts.
-The overviews of these two datasets and the meta data of orders are summarized in table \ref{tab:dat} and table \ref{tab:mdat}.
+The overviews of these two datasets and the meta data of orders are summarized in Table \ref{tab:dat} and Table \ref{tab:mdat}.
 \begin{table}[!htbp]
@@
 \begin{cases}
-1 & \mbox{if N =1}\\
-1 - \frac{index-1}{N-1} & \mbox{if N >1}
+1 & \mbox{if N = 1}\\
+1 - \frac{index-1}{N-1} & \mbox{if N $>$ 1}
 \end{cases}
@@
 \end{equation}\par
-Since we treat every account as a corpus, so a probabilistic distribution list is generated for all passengers contained in the account.
+Since we treat every account as a corpus, a probabilistic distribution list is generated for all passengers contained in the account.
 At the first stage, we need to decide the passenger number for each test order.
@@
 We denote predicted passenger list as $P'$, actual passenger list as $A$.
-Thus we can get the prediction accuracy by Equation \ref{eq:10}.
+Thus we can get the prediction accuracy by Eq.\ref{eq:10}.
 The numerator is the number of hit passengers, the denominator is penalty item for the size of predicted passenger list and predicted passenger list.
@@
 We train a probabilistic model for every account where topic number selected varying ${5,10,\dots,50}$.
-We pick a test order for each account as a new document, then predict every passenger's probability of placing this order by Equation \ref{eq:5}.
-According to above evaluating metrics, the mean prediction accuracy rate of (a) real dataset and (b) artificial dataset is shown in Figure \ref{fig:pred}.
+We pick a test order for each account as a new document, then predict every passenger's probability of placing this order by Eq.\ref{eq:5}.
+According to above evaluating metrics, the mean prediction accuracy rate of (a) real dataset and (b) artificial dataset is shown in Fig.\ref{fig:pred}.
 The left sub-figure is the evaluation result on the real dataset and the right one is on the artificial dataset.
@@
 Besides, when the topic number is 10 or 15, both datasets get the best performance while the performance goes down with the topic number increasing, which demonstrates that the size of corpus' vocabulary and number of words in each order also impact the optimal topic number.
-In the next subsection, we evaluate the recommendation performance with topic number fixed at 10.\par
+We will evaluate the recommendation performance with topic number fixed at 10.\par
 
